---
title: Appendectomy
author: Alexander Nielson
date: '2020-12-31'
slug: appendectomy.en-us
categories:
  - Major Surgery
tags:
  - Appendectomy
keywords:
  - tech
---


# Introduction

In this section we will:
* identify which Appendectomy procedures were excluded and why
* identify which different Appendectomy subgroups were created and why


If you have questions or concerns about this data please contact Alexander Nielson (alexnielson@utah.gov)


# Load Libraries
Load Libraries
```{r, message=FALSE}
library(data.table)
library(tidyverse)
library(stringi)
library(ggridges)
library(broom)
library(disk.frame)
library(RecordLinkage)
library(googlesheets4)
library(bigrquery)
library(DBI)
devtools::install_github("utah-osa/hcctools2", upgrade="never" )
library(hcctools2)
```

Establish color palettes

```{r}
cust_color_pal1 <- c(
        "Anesthesia" = "#f3476f",
        "Facility" = "#e86a33",
        "Medicine Proc" = "#e0a426",
        "Pathology" = "#77bf45",
        "Radiology" = "#617ff7",
        "Surgery" = "#a974ee"
    )

cust_color_pal2 <- c(
        "TRUE" = "#617ff7",
        "FALSE" = "#e0a426"
    )

cust_color_pal3 <- c(
        "above avg" = "#f3476f",
        "avg" = "#77bf45",
        "below avg" = "#a974ee"
    )



  fac_ref_regex <- "(UTAH)|(IHC)|(HOSP)|(HOSPITAL)|(CLINIC)|(ANESTH)|(SCOPY)|(SURG)|(LLC)|(ASSOC)|(MEDIC)|(CENTER)|(ASSOCIATES)|(U OF U)|(HEALTH)|(OLOGY)|(OSCOPY)|(FAMILY)|(VAMC)|(SLC)|(SALT LAKE)|(CITY)|(PROVO)|(OGDEN)|(ENDO )|( VALLEY)|( REGIONAL)|( CTR)|(GRANITE)|( INSTITUTE)|(INSTACARE)|(WASATCH)|(COUNTY)|(PEDIATRIC)|(CORP)|(CENTRAL)|(URGENT)|(CARE)|(UNIV)|(ODYSSEY)|(MOUNTAINSTAR)|( ORTHOPEDIC)|(INSTITUT)|(PARTNERSHIP)|(PHYSICIAN)|(CASTLEVIEW)|(CONSULTING)|(MAGEMENT)|(PRACTICE)|(EMERGENCY)|(SPECIALISTS)|(DIVISION)|(GUT WHISPERER)|(INTERMOUNTAIN)|(OBGYN)"
```

# Connect to GCP database
```{r}
bigrquery::bq_auth(path = 'D:/gcp_keys/healthcare-compare-prod-95b3b7349c32.json')

# set my project ID and dataset name
project_id <- 'healthcare-compare-prod'
dataset_name <- 'healthcare_compare'

con <- dbConnect(
  bigrquery::bigquery(),
  project = project_id,
  dataset = dataset_name,
  billing = project_id
)
```


# Get NPI table
```{r}
query <-  paste0("SELECT npi, clean_name, osa_group, osa_class, osa_specialization
                 FROM `healthcare-compare-prod.healthcare_compare.npi_full`")

#bq_project_query(billing, query) # uncomment to determine billing price for above query.

npi_full <- dbGetQuery(con, query) %>%
  data.table()
```


# get a subset of the NPI providers based upon taxonomy groups
```{r}
gs4_auth(email="alexnielson@utah.gov")
```


```{r}
surgery <- read_sheet("https://docs.google.com/spreadsheets/d/1GY8lKwUJuPHtpUl4EOw9eriLUDG9KkNWrMbaSnA5hOU/edit#gid=0",
                    sheet="major_surgery") %>% as.data.table
surgery <-  surgery[is.na(Remove) ] %>% .[["NUCC Classification"]]
```

```{r}
  npi_prov_pair <-  npi_full[osa_class %in% surgery] %>%
    .[,.(npi=npi,
         clean_name = clean_name
         )
      ]
```


# Load Data

```{r}
bun_proc <-  disk.frame("full_apcd.df")
```


```{r}
apendx <- bun_proc[surg_bun_t_appendectomy==T]
```

```{r}
apendx <-  apendx[,`:=`(
  surg_sp_name_clean = surg_sp_npi %>% map_chr(get_npi_standard_name),
  surg_bp_name_clean = surg_bp_npi %>% map_chr(get_npi_standard_name),

  medi_sp_name_clean = medi_sp_npi %>% map_chr(get_npi_standard_name),
  medi_bp_name_clean = medi_bp_npi %>% map_chr(get_npi_standard_name),

  radi_sp_name_clean = radi_sp_npi %>% map_chr(get_npi_standard_name),
  radi_bp_name_clean = radi_bp_npi %>% map_chr(get_npi_standard_name),

  path_sp_name_clean = path_sp_npi %>% map_chr(get_npi_standard_name),
  path_bp_name_clean = path_bp_npi %>% map_chr(get_npi_standard_name),

  anes_sp_name_clean = anes_sp_npi %>% map_chr(get_npi_standard_name),
  anes_bp_name_clean = anes_bp_npi %>% map_chr(get_npi_standard_name),

  faci_sp_name_clean = faci_sp_npi %>% map_chr(get_npi_standard_name),
  faci_bp_name_clean = faci_bp_npi %>% map_chr(get_npi_standard_name)
  )]
```

```{r}
apendx %>% saveRDS("apendx.RDS")
```

```{r}
apendx <- readRDS("apendx.RDS")
```


examine appendectomy median price distribution and get the highly correlated tags

```{r}
apendx %>% plot_med_density() %>% print()
apendx %>% get_tag_cor() %>% print()
```

```{r}
apendx[surg_bun_t_lung==T] %>% nrow()
```

```{r}
apendx[radi_bun_t_brain==T] %>% nrow()
```


```{r}
apendx[cnt > 4 & faci_bun_sum_med > 1000 & surg_bun_t_lung==F & radi_bun_t_brain==F] %>% nrow()
apendx[cnt > 4 & faci_bun_sum_med > 1000 & surg_bun_t_lung==F & radi_bun_t_brain==F] %>% plot_med_density() %>% print()
apendx[cnt > 4 & faci_bun_sum_med > 1000 & surg_bun_t_lung==F & radi_bun_t_brain==F] %>% get_tag_cor() %>% print()
```


```{r}
apendx <- apendx[cnt > 4 & faci_bun_sum_med > 1000 & surg_bun_t_lung==F & radi_bun_t_brain==F]
```


```{r}
apendx %>% get_tag_density_information("medi_bun_t_sodium") %>% print()
```

```{r}
apendx_w_sodium <- apendx[medi_bun_t_sodium == T & medi_bun_t_inject == T]
apendx_n_sodium <- apendx[medi_bun_t_sodium == F & medi_bun_t_inject == F]

```


## appendectomy with sodium injection
-usually antibiotics or anesthesia

examine the median price density and the highly correlated tags

```{r}
apendx_w_sodium %>% plot_med_density() %>% print()
apendx_w_sodium %>% get_tag_cor() %>% print()
```

```{r}
apendx_w_sodium[medi_bun_t_flu==T] %>% nrow()
apendx_w_sodium[surg_bun_t_removal==T] %>% nrow()
apendx_w_sodium[faci_bun_t_critical==T] %>% nrow()
apendx_w_sodium[path_bun_t_immuno==T] %>% nrow()
```

```{r}
apendx_w_sodium <- apendx_w_sodium[medi_bun_t_flu==F& surg_bun_t_removal==F & faci_bun_t_critical==F & path_bun_t_immuno==F ]
```



examine the median price density and the highly correlated tags

```{r}
apendx_w_sodium %>% plot_med_density() %>% print()
apendx_w_sodium %>% get_tag_cor() %>% print()
```

```{r}
apendx_w_sodium %>% get_tag_density_information("faci_bun_t_emergency") %>% print()
```

### at emergency department

```{r}
apendx_w_sodium_at_emerg <- apendx_w_sodium[faci_bun_t_emergency==T]
```

examine the median price density and the highly correlated tags

```{r}
apendx_w_sodium_at_emerg %>% plot_med_density() %>% print()
apendx_w_sodium_at_emerg %>% get_tag_cor() %>% print()
```

```{r}
apendx_w_sodium_at_emerg[path_bun_t_alkaline==T] %>% nrow()
apendx_w_sodium_at_emerg[medi_bun_t_solution==T] %>% nrow()
apendx_w_sodium_at_emerg[path_bun_t_typing==T] %>% nrow()
apendx_w_sodium_at_emerg[surg_bun_t_bowel==T] %>% nrow()
apendx_w_sodium_at_emerg[path_bun_t_antibod==T] %>% nrow()
apendx_w_sodium_at_emerg[radi_bun_t_mri==T] %>% nrow()
apendx_w_sodium_at_emerg[faci_bun_t_consultation==T] %>% nrow()
```

```{r}
apendx_w_sodium_at_emerg <- apendx_w_sodium_at_emerg[path_bun_t_alkaline==F & path_bun_t_typing==F & surg_bun_t_bowel==F & faci_bun_t_consultation==F ]
```

examine the median price density and the highly correlated tags

```{r}
apendx_w_sodium_at_emerg %>% plot_med_density() %>% print()
apendx_w_sodium_at_emerg %>% get_tag_cor() %>% print()
```


```{r}
apendx_w_sodium_at_emerg_btbv4 <- apendx_w_sodium_at_emerg %>% btbv4()
```

```{r}
apendx_w_sodium_at_emerg_bq <- apendx_w_sodium_at_emerg_btbv4[,
                     primary_doctor := pmap(.l=list(doctor_npi1=doctor_npi_str1,
                                  doctor_npi2=doctor_npi_str2,
                                  class_reqs="Surgery"#,
                                  # specialization_reqs = ""
                                  ),
                                                .f=calculate_primary_doctor) %>% as.character()
                     ] %>%
  #Filter out any procedures where our doctors fail both criteria.
  .[!(primary_doctor %in% c("BOTH_DOC_FAIL_CRIT", "TWO_FIT_ALL_SPECS", "NONE_FIT_SPEC_REQ"))] %>%
  .[,primary_doctor_npi := fifelse(primary_doctor==doctor_str1,
                                   doctor_npi_str1,
                                   doctor_npi_str2)] %>%
  .[,`:=`(procedure_type=7, procedure_modifier="At Emergency Department")]
```



```{r}
apendx_w_sodium_at_emerg_bq <- apendx_w_sodium_at_emerg_bq[,.(
primary_doctor,
primary_doctor_npi,
most_important_fac	,
most_important_fac_npi,
procedure_type,
procedure_modifier,
tp_med_med,
tp_med_surg,
tp_med_medi,
tp_med_path,
tp_med_radi,
tp_med_anes,
tp_med_faci,
ingest_date = Sys.Date()
)]
```


```{r, eval=FALSE}
bq_table_upload(x=procedure_table, values= apendx_w_sodium_at_emerg_bq, create_disposition='CREATE_IF_NEEDED', write_disposition='WRITE_APPEND')
```



### not at emergecny department
```{r}
apendx_w_sodium_n_emerg <- apendx_w_sodium[faci_bun_t_emergency==F]
```

examine the median price density and the highly correlated tags

```{r}
apendx_w_sodium_n_emerg %>% plot_med_density() %>% print()
apendx_w_sodium_n_emerg %>% get_tag_cor() %>% print()
```

## appendectomy no sodium injection


```{r}
apendx_n_sodium %>% plot_med_density() %>% print()
apendx_n_sodium %>% get_tag_cor() %>% print()
```

```{r}
apendx_n_sodium[surg_bun_t_bladder==T] %>% nrow()
apendx_n_sodium[surg_bun_t_gallbladder==T] %>% nrow()
apendx_n_sodium[surg_bun_t_cystoscopy==T] %>% nrow()
apendx_n_sodium[surg_bun_t_bowel==T] %>% nrow()
apendx_n_sodium[surg_bun_t_removal==T] %>% nrow()
apendx_n_sodium[surg_bun_t_cyst==T] %>% nrow()
apendx_n_sodium[`surg_bun_t_add-on`==T] %>% nrow()
apendx_n_sodium[surg_bun_t_pancreas==T] %>% nrow()
apendx_n_sodium[surg_bun_t_renal==T] %>% nrow()
apendx_n_sodium[surg_bun_t_pancreas==T] %>% nrow()
apendx_n_sodium[surg_bun_t_lap==F] %>% nrow()
apendx_n_sodium[surg_bun_t_fluid==T] %>% nrow()
apendx_n_sodium[surg_bun_t_imag==T] %>% nrow()
apendx_n_sodium[surg_bun_t_colon==T] %>% nrow()
apendx_n_sodium[surg_bun_t_partial==T] %>% nrow()
apendx_n_sodium[surg_bun_t_ovarian==T] %>% nrow()
apendx_n_sodium[surg_bun_t_implant==T] %>% nrow()
```


```{r}
apendx_n_sodium <- apendx_n_sodium[surg_bun_t_bladder==F &
                   surg_bun_t_gallbladder==F &
                   surg_bun_t_cystoscopy==F &
                   surg_bun_t_bowel==F &
                   surg_bun_t_removal==F &
                   surg_bun_t_cyst==F &
                   `surg_bun_t_add-on`==F &
                   surg_bun_t_pancreas==F &
                   surg_bun_t_renal==F &
                   surg_bun_t_pancreas==F &
                   surg_bun_t_lap==T &
                   surg_bun_t_fluid==F &
                   surg_bun_t_imag==F &
                   surg_bun_t_colon==F &
                   surg_bun_t_partial==F &
                   surg_bun_t_partial==F &
                   surg_bun_t_implant==F
                   ]
```




```{r}
apendx_n_sodium %>% plot_med_density() %>% print()
apendx_n_sodium %>% get_tag_cor() %>% print()
```

```{r}
apendx_n_sodium %>% plot_price_vs_duration() %>% print()
```

```{r}
apendx_n_sodium[duration_mean<2] %>% plot_price_vs_duration() %>% print()
```



```{r}
apendx_n_sodium[duration_mean<2] %>% plot_med_density() %>% print()
apendx_n_sodium[duration_mean<2] %>% get_tag_cor() %>% print()
```



```{r}
apendx_n_sodium <- apendx_n_sodium[duration_mean<2]
```



```{r}
apendx_n_sodium [medi_bun_t_choline==T] %>% nrow()
```


```{r}
apendx_n_sodium[radi_bun_t_imaging==T] %>% nrow()
```


```{r}
apendx_n_sodium[medi_bun_t_saline==T] %>% nrow()
```


```{r}
apendx_n_sodium <- apendx_n_sodium[medi_bun_t_choline==F & radi_bun_t_imaging==F & medi_bun_t_saline==F]
```

```{r}
apendx_n_sodium %>% plot_med_density() %>% print()
apendx_n_sodium %>% get_tag_cor() %>% print()
```



```{r}
apendx_n_sodium[radi_bun_t_echo==T] %>% nrow()
apendx_n_sodium[radi_bun_t_exam==T] %>% nrow()
apendx_n_sodium[radi_bun_t_ct==T] %>% nrow()

```


```{r}
apendx_n_sodium_btbv4 <- apendx_n_sodium %>% btbv4()
```

```{r}
apendx_n_sodium_bq <- apendx_n_sodium_btbv4[,
                     primary_doctor := pmap(.l=list(doctor_npi1=doctor_npi_str1,
                                  doctor_npi2=doctor_npi_str2,
                                  class_reqs="Surgery"#,
                                  # specialization_reqs = ""
                                  ),
                                                .f=calculate_primary_doctor) %>% as.character()
                     ] %>%
  #Filter out any procedures where our doctors fail both criteria.
  .[!(primary_doctor %in% c("BOTH_DOC_FAIL_CRIT", "TWO_FIT_ALL_SPECS", "NONE_FIT_SPEC_REQ"))] %>%
  .[,primary_doctor_npi := fifelse(primary_doctor==doctor_str1,
                                   doctor_npi_str1,
                                   doctor_npi_str2)] %>%
  .[,`:=`(procedure_type=7, procedure_modifier="Standard")]
```



```{r}
apendx_n_sodium_bq <- apendx_n_sodium_bq[,.(
primary_doctor,
primary_doctor_npi,
most_important_fac	,
most_important_fac_npi,
procedure_type,
procedure_modifier,
tp_med_med,
tp_med_surg,
tp_med_medi,
tp_med_path,
tp_med_radi,
tp_med_anes,
tp_med_faci,
ingest_date = Sys.Date()
)]
```


```{r}
apendx_n_sodium_bq <- apendx_n_sodium_bq[,
                            primary_doctor_npi := fifelse(primary_doctor=="ALEXANDER LORENZO COLONNA",
                                         "1568659324",
                                         primary_doctor_npi)]
```

```{r, eval=FALSE}
bq_table_upload(x=procedure_table, values= apendx_n_sodium_bq, create_disposition='CREATE_IF_NEEDED', write_disposition='WRITE_APPEND')
```

