---
title: Hernia Repair
author: Alexander Nielson
date: '2020-12-30'
slug: hernia-repair.en-us
categories:
  - Major Surgery
tags:
  - Hernia
  - Repair
keywords:
  - tech
---

# Introduction

In this section we will:
* identify which Hernia Repair procedures were excluded and why
* identify which different Hernia Repair subgroups were created and why


If you have questions or concerns about this data please contact Alexander Nielson (alexnielson@utah.gov)


# Load Libraries
Load Libraries
```{r, message=FALSE}
library(data.table)
library(tidyverse)
library(stringi)
library(ggridges)
library(broom)
library(disk.frame)
library(RecordLinkage)
library(googlesheets4)
library(bigrquery)
library(DBI)
devtools::install_github("utah-osa/hcctools2", upgrade="never" )
library(hcctools2)
```

Establish color palettes

```{r}
cust_color_pal1 <- c(
        "Anesthesia" = "#f3476f",
        "Facility" = "#e86a33",
        "Medicine Proc" = "#e0a426",
        "Pathology" = "#77bf45",
        "Radiology" = "#617ff7",
        "Surgery" = "#a974ee"
    )

cust_color_pal2 <- c(
        "TRUE" = "#617ff7",
        "FALSE" = "#e0a426"
    )

cust_color_pal3 <- c(
        "above avg" = "#f3476f",
        "avg" = "#77bf45",
        "below avg" = "#a974ee"
    )



  fac_ref_regex <- "(UTAH)|(IHC)|(HOSP)|(HOSPITAL)|(CLINIC)|(ANESTH)|(SCOPY)|(SURG)|(LLC)|(ASSOC)|(MEDIC)|(CENTER)|(ASSOCIATES)|(U OF U)|(HEALTH)|(OLOGY)|(OSCOPY)|(FAMILY)|(VAMC)|(SLC)|(SALT LAKE)|(CITY)|(PROVO)|(OGDEN)|(ENDO )|( VALLEY)|( REGIONAL)|( CTR)|(GRANITE)|( INSTITUTE)|(INSTACARE)|(WASATCH)|(COUNTY)|(PEDIATRIC)|(CORP)|(CENTRAL)|(URGENT)|(CARE)|(UNIV)|(ODYSSEY)|(MOUNTAINSTAR)|( ORTHOPEDIC)|(INSTITUT)|(PARTNERSHIP)|(PHYSICIAN)|(CASTLEVIEW)|(CONSULTING)|(MAGEMENT)|(PRACTICE)|(EMERGENCY)|(SPECIALISTS)|(DIVISION)|(GUT WHISPERER)|(INTERMOUNTAIN)|(OBGYN)"
```

# Connect to GCP database
```{r}
bigrquery::bq_auth(path = 'D:/gcp_keys/healthcare-compare-prod-95b3b7349c32.json')

# set my project ID and dataset name
project_id <- 'healthcare-compare-prod'
dataset_name <- 'healthcare_compare'

con <- dbConnect(
  bigrquery::bigquery(),
  project = project_id,
  dataset = dataset_name,
  billing = project_id
)
```


# Get NPI table
```{r}
query <-  paste0("SELECT npi, clean_name, osa_group, osa_class, osa_specialization
                 FROM `healthcare-compare-prod.healthcare_compare.npi_full`")

#bq_project_query(billing, query) # uncomment to determine billing price for above query.

npi_full <- dbGetQuery(con, query) %>%
  data.table()
```


# get a subset of the NPI providers based upon taxonomy groups
```{r}
gs4_auth(email="alexnielson@utah.gov")
```


```{r}
surgery <- read_sheet("https://docs.google.com/spreadsheets/d/1GY8lKwUJuPHtpUl4EOw9eriLUDG9KkNWrMbaSnA5hOU/edit#gid=0",
                    sheet="major_surgery") %>% as.data.table
surgery <-  surgery[is.na(Remove) ] %>% .[["NUCC Classification"]]
```

```{r}
  npi_prov_pair <-  npi_full[osa_class %in% surgery] %>%
    .[,.(npi=npi,
         clean_name = clean_name
         )
      ]
```


# Load Data

```{r}
bun_proc <-  disk.frame("full_apcd.df")
```



```{r}
hernia <- bun_proc[surg_bun_descr %>% stri_detect_regex("hern")]
```


```{r}
hernia <-  hernia[,`:=`(
  surg_sp_name_clean = surg_sp_npi %>% map_chr(get_npi_standard_name),
  surg_bp_name_clean = surg_bp_npi %>% map_chr(get_npi_standard_name),
  
  medi_sp_name_clean = medi_sp_npi %>% map_chr(get_npi_standard_name),
  medi_bp_name_clean = medi_bp_npi %>% map_chr(get_npi_standard_name),
  
  radi_sp_name_clean = radi_sp_npi %>% map_chr(get_npi_standard_name),
  radi_bp_name_clean = radi_bp_npi %>% map_chr(get_npi_standard_name),
  
  path_sp_name_clean = path_sp_npi %>% map_chr(get_npi_standard_name),
  path_bp_name_clean = path_bp_npi %>% map_chr(get_npi_standard_name),
  
  anes_sp_name_clean = anes_sp_npi %>% map_chr(get_npi_standard_name),
  anes_bp_name_clean = anes_bp_npi %>% map_chr(get_npi_standard_name),
  
  faci_sp_name_clean = faci_sp_npi %>% map_chr(get_npi_standard_name),
  faci_bp_name_clean = faci_bp_npi %>% map_chr(get_npi_standard_name)
  )]
```

<!-- ```{r} -->
<!-- hernia_btbv4 <- hernia %>% btbv4() -->
<!-- ``` -->


<!-- ```{r} -->
<!-- hernia_bq <- hernia_btbv4[, -->
<!--                      primary_doctor := pmap(.l=list(doctor_npi1=doctor_npi_str1, -->
<!--                                   doctor_npi2=doctor_npi_str2, -->
<!--                                   class_reqs="Surgery"#, -->
<!--                                   # specialization_reqs = "" -->
<!--                                   ), -->
<!--                                                 .f=calculate_primary_doctor) %>% as.character() -->
<!--                      ] %>%  -->
<!--   #Filter out any procedures where our doctors fail both criteria.  -->
<!--   .[!(primary_doctor %in% c("BOTH_DOC_FAIL_CRIT", "TWO_FIT_ALL_SPECS", "NONE_FIT_SPEC_REQ"))] %>%  -->
<!--   .[,primary_doctor_npi := fifelse(primary_doctor==doctor_str1, -->
<!--                                    doctor_npi_str1, -->
<!--                                    doctor_npi_str2)] %>%  -->
<!--   .[,`:=`(procedure_type=6, procedure_modifier="Hernia Repair")] -->
<!-- ``` -->

<!-- ```{r} -->
<!-- hernia_bq %>% count(most_important_fac) %>% arrange(desc(n)) %>% View() -->
<!-- ``` -->



<!-- hernia -->

<!-- ```{r} -->
<!-- hernia %>% .[["facility_str"]] %>% stri_split_regex(",") %>% unlist() %>% stri_trim_both()  %>% sort() %>% table() %>% View() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- hernia_btbv4 %>% count(most_important_fac) %>% arrange(desc(n)) %>% View() -->
<!-- ``` -->




```{r}
hernia %>% plot_med_density() %>% print()
hernia %>% get_tag_cor() %>% print()
```

```{r}
hernia %>% plot_price_vs_duration() %>% print()
```


```{r}
hernia <- hernia[duration_mean<2 & tp_med > 0 & tp_med < 50000 & faci_bun_sum_med > 500]
```


```{r}
hernia %>% plot_med_density() %>% print()
hernia %>% get_tag_cor() %>% print()
```

```{r}
hernia %>% get_tag_density_information("surg_bun_t_lap") %>% print()
```

```{r}
hernia_lap <- hernia[surg_bun_t_lap ==T]
hernia_n_lap <- hernia[surg_bun_t_lap==F]
```

# hernia_lap
```{r}
hernia_lap %>% plot_med_density() %>% print()
hernia_lap %>% get_tag_cor() %>% print()
```

```{r}

hernia_lap %>% get_tag_density_information("medi_bun_t_sodium" ) %>% print()
```

```{r}
hernia_lap <- hernia_lap[medi_bun_t_sodium == T]
```

```{r}
hernia_lap %>% get_tag_density_information("surg_bun_t_esoph" ) %>% print()
```

```{r}
hernia_lap <- hernia_lap[surg_bun_t_esoph==F]
```

```{r}
hernia_lap %>% plot_med_density() %>% print()
hernia_lap %>% get_tag_cor() %>% print()
```

```{r}
hernia_lap %>% get_tag_density_information("surg_bun_t_lymph") %>% print()
```

```{r}
hernia_lap <- hernia_lap[surg_bun_t_lymph==F]
```


```{r, eval=FALSE}
hernia_lap %>% get_tag_density_information("surg_bun_t_urethra") %>% print()
```

```{r}
hernia_lap <- hernia_lap[surg_bun_t_urethra==F]
```


```{r}
hernia_lap %>% get_tag_density_information("surg_bun_t_prostate") %>% print()
```

```{r}
hernia_lap <- hernia_lap[surg_bun_t_prostate==F]
```


```{r}
hernia_lap %>% plot_med_density() %>% print()
hernia_lap %>% get_tag_cor() %>% print()
```

```{r}
hernia_lap %>% get_tag_density_information("surg_bun_t_graft") %>% print()
```

```{r}
hernia_lap <- hernia_lap[surg_bun_t_graft==F]
```

```{r}
hernia_lap %>% get_tag_density_information("surg_bun_t_block") %>% print()
```

```{r}
hernia_lap <- hernia_lap[surg_bun_t_block==F]
```


```{r}
# hernia_lap %>% get_tag_density_information("surg_bun_t_skin") %>% print()
```
```{r}
hernia_lap <- hernia_lap[surg_bun_t_skin==F]
```


```{r}
hernia_lap %>% plot_med_density() %>% print()
hernia_lap %>% get_tag_cor() %>% print()
```

```{r}
# hernia_lap %>% get_tag_density_information("surg_bun_t_injection") %>% print()
hernia_lap %>% get_tag_density_information("anes_bun_t_upper") %>% print()
hernia_lap %>% get_tag_density_information("anes_bun_t_kidney") %>% print()
hernia_lap %>% get_tag_density_information("anes_bun_t_ureter") %>% print()
hernia_lap %>% get_tag_density_information("surg_bun_t_ant") %>% print()
hernia_lap %>% get_tag_density_information("path_bun_t_complete") %>% print()
```


```{r}
hernia_lap <- hernia_lap[surg_bun_t_injection ==F & anes_bun_t_kidney == F & anes_bun_t_ureter==F & surg_bun_t_ant==F ]
```

```{r}
hernia_lap %>% plot_med_density() %>% print()
hernia_lap %>% get_tag_cor() %>% print()
```

hernia_lap = surg_bun_t_uters
```{r}
hernia_lap <- hernia_lap[surg_bun_t_uterus == F & surg_bun_t_uterus==F ]
```

```{r}
hernia_lap %>% plot_med_density() %>% print()
hernia_lap %>% get_tag_cor() %>% print()
```

```{r}
hernia_lap_btbv4 <- hernia_lap %>% btbv4() %>% .[,
                     primary_doctor := pmap(.l=list(doctor_npi1=doctor_npi_str1,
                                  doctor_npi2=doctor_npi_str2,
                                  class_reqs="Surgery"#,
                                  # specialization_reqs = ""
                                  ),
                                                .f=calculate_primary_doctor) %>% as.character()
                     ] %>% 
  #Filter out any procedures where our doctors fail both criteria. 
  .[!(primary_doctor %in% c("BOTH_DOC_FAIL_CRIT", "TWO_FIT_ALL_SPECS", "NONE_FIT_SPEC_REQ"))] %>% 
  .[,primary_doctor_npi := fifelse(primary_doctor==doctor_str1,
                                   doctor_npi_str1,
                                   doctor_npi_str2)] %>% 
  .[,`:=`(procedure_type=6, procedure_modifier="Hernia Laparoscopy Repair")]
```

```{r, eval=FALSE}
hernia_lap_btbv4 %>% count(most_important_fac) %>% arrange(desc(n)) %>% View()
```



# herna_n_lap 

```{r}
hernia_n_lap %>% plot_med_density() %>% print()
hernia_n_lap %>% get_tag_cor() %>% print()
```

```{r}
hernia_n_lap %>% get_tag_density_information("faci_bun_t_hospital") %>% print()
```

```{r}
hernia_n_lap <-  hernia_n_lap[faci_bun_t_hospital==F]
```



```{r}
hernia_n_lap %>% get_tag_density_information("surg_bun_t_skin") %>% print()
```

```{r}
hernia_n_lap <- hernia_n_lap[surg_bun_t_skin == F & surg_bun_t_graft==F ]
```

```{r}
hernia_n_lap %>% plot_med_density() %>% print()
hernia_n_lap %>% get_tag_cor() %>% print()
```


```{r}
hernia_n_lap %>% get_tag_density_information("surg_bun_t_esoph") %>% print()
```

```{r}
hernia_n_lap <- hernia_n_lap[surg_bun_t_esoph == F]
```


```{r}
hernia_n_lap %>% get_tag_density_information("radi_bun_t_chest") %>% print()
```

```{r}
hernia_n_lap <- hernia_n_lap[radi_bun_t_chest == F]
```


```{r}
hernia_n_lap %>% get_tag_density_information("radi_bun_t_contrast") %>% print()
```

```{r}
hernia_n_lap <- hernia_n_lap[radi_bun_t_contrast == F]
```


```{r}
hernia_n_lap %>% get_tag_density_information("surg_bun_t_umbil") %>% print()
```

```{r}
hernia_n_lap %>% plot_med_density() %>% print()
hernia_n_lap %>% get_tag_cor() %>% print()
```

```{r}
hernia_n_lap[surg_bun_t_arthroscopy==T] %>% nrow() #%>% get_tag_density_information("surg_bun_t_arthroscopy") %>% print()
hernia_n_lap[surg_bun_t_uterus==T] %>% nrow()
hernia_n_lap[path_bun_t_typing==T] %>% nrow()
hernia_n_lap[path_bun_t_anti==T] %>% nrow()
hernia_n_lap[path_bun_t_tissue==T] %>% nrow()
hernia_n_lap[surg_bun_t_interlaminar==T] %>% nrow()
hernia_n_lap[faci_bun_t_est==T] %>% nrow()
hernia_n_lap[path_bun_t_urinalysis==T] %>% nrow()
```

```{r}
hernia_n_lap <- hernia_n_lap[surg_bun_t_arthroscopy==F & surg_bun_t_uterus==F & path_bun_t_typing==F & path_bun_t_anti==F & surg_bun_t_interlaminar==F & path_bun_t_urinalysis==F]
```

```{r}
hernia_n_lap %>% plot_med_density() %>% print()
hernia_n_lap %>% get_tag_cor() %>% print()
```

```{r}
hernia_n_lap %>% get_tag_density_information("path_bun_t_patho") %>% print()
```

```{r}
hernia_n_lap <- hernia_n_lap[path_bun_t_patho==F]
```


```{r}
hernia_n_lap %>% get_tag_density_information("medi_bun_t_normal") %>% print()
```

```{r}
hernia_n_lap <- hernia_n_lap[medi_bun_t_normal==F]
```


```{r}
hernia_n_lap %>% plot_med_density() %>% print()
hernia_n_lap %>% get_tag_cor() %>% print()
```

```{r}
hernia_n_lap[surg_bun_t_tumor==T] %>% nrow()
hernia_n_lap[surg_bun_t_injection==T] %>% nrow()
hernia_n_lap[medi_bun_t_splt==T] %>% nrow()
hernia_n_lap[surg_bun_t_revise==T] %>% nrow()
hernia_n_lap[surg_bun_t_ablate==T] %>% nrow()
hernia_n_lap[surg_bun_t_ear==T] %>% nrow()
hernia_n_lap[surg_bun_t_defect==T] %>% nrow()
hernia_n_lap[anes_bun_t_abdom==T] %>% nrow()
```





```{r}
hernia_n_lap %>% get_tag_density_information("surg_bun_t_injection") %>% print()
```

```{r}
hernia_n_lap %>% get_tag_density_information("anes_bun_t_abdom") %>% print()
```

```{r}
hernia_n_lap <- hernia_n_lap[surg_bun_t_injection==F & medi_bun_t_splt==F & surg_bun_t_revise ==F & surg_bun_t_ablate==F &  surg_bun_t_ear==F & surg_bun_t_defect==F & anes_bun_t_abdom==F]
```

```{r}
hernia_n_lap %>% plot_med_density() %>% print()
hernia_n_lap %>% get_tag_cor() %>% print()
```

```{r}
hernia_n_lap <- hernia_n_lap[tp_med > 2000 & tp_med < 20000]
```

```{r}
hernia_n_lap %>% plot_med_density() %>% print()
hernia_n_lap %>% get_tag_cor() %>% print()
```
```{r}
hernia_n_lap %>% get_tag_density_information("surg_bun_t_testis") %>% print()
```

```{r}
hernia_n_lap <- hernia_n_lap[surg_bun_t_testis == F ]
```


```{r, eval=FALSE}
hernia_n_lap %>% get_tag_density_information("surg_bun_t_suspension") %>% print()
```


```{r}
hernia_n_lap <- hernia_n_lap[surg_bun_t_suspension == F ]
```


```{r}
hernia_n_lap %>% plot_med_density() %>% print()
hernia_n_lap %>% get_tag_cor() %>% print()
```


```{r}
hernia_n_lap %>% get_tag_density_information("medi_bun_t_oral") %>% print()
```

```{r}
hernia_n_lap <- hernia_n_lap[medi_bun_t_oral ==F]
```


```{r}
hernia_n_lap %>% plot_med_density() %>% print()
hernia_n_lap %>% get_tag_cor() %>% print()
```


```{r}
hernia_n_lap_btbv4 <- hernia_n_lap %>% btbv4() %>% .[,
                     primary_doctor := pmap(.l=list(doctor_npi1=doctor_npi_str1,
                                  doctor_npi2=doctor_npi_str2,
                                  class_reqs="Surgery"#,
                                  # specialization_reqs = ""
                                  ),
                                                .f=calculate_primary_doctor) %>% as.character()
                     ] %>% 
  #Filter out any procedures where our doctors fail both criteria. 
  .[!(primary_doctor %in% c("BOTH_DOC_FAIL_CRIT", "TWO_FIT_ALL_SPECS", "NONE_FIT_SPEC_REQ"))] %>% 
  .[,primary_doctor_npi := fifelse(primary_doctor==doctor_str1,
                                   doctor_npi_str1,
                                   doctor_npi_str2)] %>% 
  .[,`:=`(procedure_type=6, procedure_modifier="Hernia Repair")]
```



```{r}
hernia_full <- hernia_lap_btbv4 %>% rbind(hernia_n_lap_btbv4)
```

```{r, eval=FALSE}
hernia_full %>% count(most_important_fac) %>% arrange(desc(n)) %>% View()
```

```{r}
hernia_bq <- hernia_full %>% .[,.(tp_med_med = median(tp_med_med),
                            tp_med_surg = median(tp_med_surg),
                            tp_med_medi = median(tp_med_medi),
                            tp_med_path = median(tp_med_path),
                            tp_med_radi = median(tp_med_radi),
                            tp_med_anes = median(tp_med_anes),
                            tp_med_faci = median(tp_med_faci),
                            tp_cnt_cnt = sum(tp_cnt_cnt)
                            ),
                         by=c("procedure_type", "procedure_modifier","primary_doctor", "primary_doctor_npi", "most_important_fac", "most_important_fac_npi")] %>% 
  
  .[,.(
  primary_doctor,
  primary_doctor_npi,
  most_important_fac	,
  most_important_fac_npi,	
  procedure_type,
  procedure_modifier,
  tp_med_med,
  tp_med_surg,
  tp_med_medi,
  tp_med_path,
  tp_med_radi,
  tp_med_anes,
  tp_med_faci,
  tp_cnt_cnt,
  ingest_date = Sys.Date()
)]
```


```{r}
hernia_bq$tp_med_med %>% summary()
```


```{r}
hernia_bq %>% fwrite("2020-12-17-hernia_repiar_fixed.csv")
```


```{r}
hernia_bq <- hernia_bq[,.(
  primary_doctor,
  primary_doctor_npi,
  most_important_fac	,
  most_important_fac_npi,	
  procedure_type,
  procedure_modifier,
  tp_med_med,
  tp_med_surg,
  tp_med_medi,
  tp_med_path,
  tp_med_radi,
  tp_med_anes,
  tp_med_faci,
  ingest_date = Sys.Date()
)]
```



```{r, eval=FALSE}
bq_table_upload(x=procedure_table, values= hernia_bq, create_disposition='CREATE_IF_NEEDED', write_disposition='WRITE_APPEND')
```


