---
title: Hysterectomy
author: Alexander Nielson
date: '2020-12-31'
slug: hysterectomy.en-us
categories:
  - Major Surgery
tags:
  - Hysterectomy
  - Hyster
  - Ectomy
  - OBGYN
keywords:
  - tech
---


# Introduction

In this section we will:
* identify which Hysterectomy procedures were excluded and why
* identify which different Hysterectomy Repair subgroups were created and why


If you have questions or concerns about this data please contact Alexander Nielson (alexnielson@utah.gov)


# Load Libraries
Load Libraries
```{r, message=FALSE}
library(data.table)
library(tidyverse)
library(stringi)
library(ggridges)
library(broom)
library(disk.frame)
library(RecordLinkage)
library(googlesheets4)
library(bigrquery)
library(DBI)
devtools::install_github("utah-osa/hcctools2", upgrade="never" )
library(hcctools2)
```

Establish color palettes

```{r}
cust_color_pal1 <- c(
        "Anesthesia" = "#f3476f",
        "Facility" = "#e86a33",
        "Medicine Proc" = "#e0a426",
        "Pathology" = "#77bf45",
        "Radiology" = "#617ff7",
        "Surgery" = "#a974ee"
    )

cust_color_pal2 <- c(
        "TRUE" = "#617ff7",
        "FALSE" = "#e0a426"
    )

cust_color_pal3 <- c(
        "above avg" = "#f3476f",
        "avg" = "#77bf45",
        "below avg" = "#a974ee"
    )



  fac_ref_regex <- "(UTAH)|(IHC)|(HOSP)|(HOSPITAL)|(CLINIC)|(ANESTH)|(SCOPY)|(SURG)|(LLC)|(ASSOC)|(MEDIC)|(CENTER)|(ASSOCIATES)|(U OF U)|(HEALTH)|(OLOGY)|(OSCOPY)|(FAMILY)|(VAMC)|(SLC)|(SALT LAKE)|(CITY)|(PROVO)|(OGDEN)|(ENDO )|( VALLEY)|( REGIONAL)|( CTR)|(GRANITE)|( INSTITUTE)|(INSTACARE)|(WASATCH)|(COUNTY)|(PEDIATRIC)|(CORP)|(CENTRAL)|(URGENT)|(CARE)|(UNIV)|(ODYSSEY)|(MOUNTAINSTAR)|( ORTHOPEDIC)|(INSTITUT)|(PARTNERSHIP)|(PHYSICIAN)|(CASTLEVIEW)|(CONSULTING)|(MAGEMENT)|(PRACTICE)|(EMERGENCY)|(SPECIALISTS)|(DIVISION)|(GUT WHISPERER)|(INTERMOUNTAIN)|(OBGYN)"
```

# Connect to GCP database
```{r}
bigrquery::bq_auth(path = 'D:/gcp_keys/healthcare-compare-prod-95b3b7349c32.json')

# set my project ID and dataset name
project_id <- 'healthcare-compare-prod'
dataset_name <- 'healthcare_compare'

con <- dbConnect(
  bigrquery::bigquery(),
  project = project_id,
  dataset = dataset_name,
  billing = project_id
)
```


# Get NPI table
```{r}
query <-  paste0("SELECT npi, clean_name, osa_group, osa_class, osa_specialization
                 FROM `healthcare-compare-prod.healthcare_compare.npi_full`")

#bq_project_query(billing, query) # uncomment to determine billing price for above query.

npi_full <- dbGetQuery(con, query) %>%
  data.table()
```


# get a subset of the NPI providers based upon taxonomy groups
```{r}
gs4_auth(email="alexnielson@utah.gov")
```


```{r}
surgery <- read_sheet("https://docs.google.com/spreadsheets/d/1GY8lKwUJuPHtpUl4EOw9eriLUDG9KkNWrMbaSnA5hOU/edit#gid=0",
                    sheet="major_surgery") %>% as.data.table
surgery <-  surgery[is.na(Remove) ] %>% .[["NUCC Classification"]]
```

```{r}
  npi_prov_pair <-  npi_full[osa_class %in% surgery] %>%
    .[,.(npi=npi,
         clean_name = clean_name
         )
      ]
```


# Load Data

```{r}
bun_proc <-  disk.frame("full_apcd.df")
```


```{r}
hyst <- bun_proc[surg_bun_t_hysterectomy==T & cnt >2 & faci_bun_sum_med > 500]
```


```{r}
hyst <-  hyst[,`:=`(
  surg_sp_name_clean = surg_sp_npi %>% map_chr(get_npi_standard_name),
  surg_bp_name_clean = surg_bp_npi %>% map_chr(get_npi_standard_name),
  
  medi_sp_name_clean = medi_sp_npi %>% map_chr(get_npi_standard_name),
  medi_bp_name_clean = medi_bp_npi %>% map_chr(get_npi_standard_name),
  
  radi_sp_name_clean = radi_sp_npi %>% map_chr(get_npi_standard_name),
  radi_bp_name_clean = radi_bp_npi %>% map_chr(get_npi_standard_name),
  
  path_sp_name_clean = path_sp_npi %>% map_chr(get_npi_standard_name),
  path_bp_name_clean = path_bp_npi %>% map_chr(get_npi_standard_name),
  
  anes_sp_name_clean = anes_sp_npi %>% map_chr(get_npi_standard_name),
  anes_bp_name_clean = anes_bp_npi %>% map_chr(get_npi_standard_name),
  
  faci_sp_name_clean = faci_sp_npi %>% map_chr(get_npi_standard_name),
  faci_bp_name_clean = faci_bp_npi %>% map_chr(get_npi_standard_name)
  )]
```

```{r}
hyst %>% saveRDS(paste0("hysterectomy", Sys.Date(),".RDS"))
```



```{r}
hyst %>% plot_med_density() %>% print()
hyst %>% get_tag_cor() %>% print()
```


```{r}
hyst %>% plot_price_vs_duration() %>% print()
```


```{r}
hyst %>% get_tag_density_information("anes_bun_t_upper") %>% print()
```

```{r}
hyst <- hyst[anes_bun_t_upper==F]
```

```{r}
hyst %>% plot_med_density() %>% print()
hyst %>% get_tag_cor() %>% print()
```


```{r}
hyst <- hyst[duration_mean<3]
hyst %>% plot_med_density() %>% print()
hyst %>% get_tag_cor() %>% print()
```


```{r}
hyst %>% get_tag_density_information("anes_bun_t_deliver") %>% print()
```


```{r}
hyst <- hyst[anes_bun_t_deliver==F]
```


```{r}
hyst %>% plot_med_density() %>% print()
hyst %>% get_tag_cor() %>% print()
```

```{r}
hyst %>% get_tag_density_information("anes_bun_t_bladder") %>% print()
```

```{r}
hyst <- hyst[anes_bun_t_bladder==F]
```

```{r}
hyst %>% plot_med_density() %>% print()
hyst %>% get_tag_cor() %>% print()
```


## hyst_vag

```{r}
hyst_vag <- hyst[surg_bun_t_vag == T]
```


```{r}
hyst_vag %>% plot_med_density() %>% print()
hyst_vag %>% get_tag_cor() %>% print()
```

```{r}
hyst_vag[surg_bun_t_coloproctostomy==T] %>% nrow()
```

```{r}
hyst_vag[surg_bun_t_bladder==T] %>% nrow()
```

```{r}
hyst_vag <- hyst_vag[surg_bun_t_coloproctostomy==F & surg_bun_t_bladder==F]
```

```{r}
hyst_vag %>% plot_med_density() %>% print()
hyst_vag %>% get_tag_cor() %>% print()
```

```{r}
hyst_vag %>% get_tag_density_information("path_bun_t_without_scope") %>% print()
```

```{r}
hyst_vag <- hyst_vag[path_bun_t_without_scope==F]
```

```{r}
hyst_vag %>% get_tag_density_information("anes_bun_t_hysterectomy") %>% print()
```



```{r}
hyst_vag_btbv4 <- hyst_vag %>% btbv4()
```


```{r}
hyst_vag_bq <- hyst_vag_btbv4[,
                     primary_doctor := pmap(.l=list(doctor_npi1=doctor_npi_str1,
                                  doctor_npi2=doctor_npi_str2,
                                  class_reqs="Obstetrics & Gynecology"
                                  ),
                                                .f=calculate_primary_doctor) %>% as.character()
                     ] %>% 
  #Filter out any procedures where our doctors fail both criteria. 
  .[!(primary_doctor %in% c("BOTH_DOC_FAIL_CRIT", "TWO_FIT_ALL_SPECS"))] %>% 
  .[,primary_doctor_npi := fifelse(primary_doctor==doctor_str1,
                                   doctor_npi_str1,
                                   doctor_npi_str2)] %>% 
  .[,`:=`(
    procedure_type=4,
    procedure_modifier = "Vaginal Hysterectomy"
  )]
```


```{r}
hyst_vag_bq <- hyst_vag_bq[,.(
primary_doctor,
primary_doctor_npi,
most_important_fac	,
most_important_fac_npi,	
procedure_type,
procedure_modifier,
tp_med_med,
tp_med_surg,
tp_med_medi,
tp_med_path,
tp_med_radi,
tp_med_anes,
tp_med_faci,
ingest_date = Sys.Date()
)]
```

```{r, eval=FALSE}
bq_table_upload(x=procedure_table, values= hyst_vag_bq, create_disposition='CREATE_IF_NEEDED', write_disposition='WRITE_APPEND')
```




## hyst_total 

```{r}
hyst_total <- hyst[surg_bun_t_total == T]
```

```{r}
hyst_total %>% plot_med_density() %>% print()
hyst_total %>% get_tag_cor() %>% print()
```

```{r}
hyst_total %>% get_tag_density_information("path_bun_t_tumor") %>% print()
```


```{r}
hyst_total <- hyst_total[surg_bun_t_colon==F & surg_bun_t_partial==F & path_bun_t_tumor==F & surg_bun_t_renal==F ]
```


```{r}
hyst_total %>% plot_med_density() %>% print()
hyst_total %>% get_tag_cor() %>% print()
```

```{r}
# hyst_total %>% get_tag_density_information("surg_bun_t_complex") %>% print()
```

```{r}
hyst_total %>% get_tag_density_information("surg_bun_t_remove") %>% print()
```

```{r}
hyst_total <- hyst_total[surg_bun_t_remove==F & surg_bun_t_complex==F & surg_bun_t_drain==F & surg_bun_t_skin==F ]
```



```{r}
hyst_total %>% plot_med_density() %>% print()
hyst_total %>% get_tag_cor() %>% print()
```


```{r}
hyst_total_btbv4 <- hyst_total %>% btbv4()
```


```{r}
hyst_total_bq <- hyst_total_btbv4[,
                     primary_doctor := pmap(.l=list(doctor_npi1=doctor_npi_str1,
                                  doctor_npi2=doctor_npi_str2,
                                  class_reqs="Obstetrics & Gynecology"
                                  ),
                                                .f=calculate_primary_doctor) %>% as.character()
                     ] %>% 
  #Filter out any procedures where our doctors fail both criteria. 
  .[!(primary_doctor %in% c("BOTH_DOC_FAIL_CRIT", "TWO_FIT_ALL_SPECS"))] %>% 
  .[,primary_doctor_npi := fifelse(primary_doctor==doctor_str1,
                                   doctor_npi_str1,
                                   doctor_npi_str2)] %>% 
  .[,`:=`(
    procedure_type=4,
    procedure_modifier = "Total Hysterectomy"
  )]
```


```{r}
hyst_total_bq <- hyst_total_bq[,.(
primary_doctor,
primary_doctor_npi,
most_important_fac	,
most_important_fac_npi,	
procedure_type,
procedure_modifier,
tp_med_med,
tp_med_surg,
tp_med_medi,
tp_med_path,
tp_med_radi,
tp_med_anes,
tp_med_faci,
ingest_date = Sys.Date()
)]
```


```{r, eval=F}
bq_table_upload(x=procedure_table, values= hyst_total_bq, create_disposition='CREATE_IF_NEEDED', write_disposition='WRITE_APPEND')
```

