---
title: Birth
author: Alexander Nielson
date: '2020-12-31'
slug: birth.en-us
categories:
  - Major Surgery
tags:
  - Caesarian Section
  - VBAC
  - Vaginal Birth
keywords:
  - tech
---


# Introduction

In this section we will:
* identify which Delivery procedures were excluded and why
* identify which different Delivery subgroups were created and why


If you have questions or concerns about this data please contact Alexander Nielson (alexnielson@utah.gov)


# Load Libraries
Load Libraries
```{r, message=FALSE}
library(data.table)
library(tidyverse)
library(stringi)
library(ggridges)
library(broom)
library(disk.frame)
library(RecordLinkage)
library(googlesheets4)
library(bigrquery)
library(DBI)
devtools::install_github("utah-osa/hcctools2", upgrade="never" )
library(hcctools2)
```

Establish color palettes

```{r}
cust_color_pal1 <- c(
        "Anesthesia" = "#f3476f",
        "Facility" = "#e86a33",
        "Medicine Proc" = "#e0a426",
        "Pathology" = "#77bf45",
        "Radiology" = "#617ff7",
        "Surgery" = "#a974ee"
    )

cust_color_pal2 <- c(
        "TRUE" = "#617ff7",
        "FALSE" = "#e0a426"
    )

cust_color_pal3 <- c(
        "above avg" = "#f3476f",
        "avg" = "#77bf45",
        "below avg" = "#a974ee"
    )



  fac_ref_regex <- "(UTAH)|(IHC)|(HOSP)|(HOSPITAL)|(CLINIC)|(ANESTH)|(SCOPY)|(SURG)|(LLC)|(ASSOC)|(MEDIC)|(CENTER)|(ASSOCIATES)|(U OF U)|(HEALTH)|(OLOGY)|(OSCOPY)|(FAMILY)|(VAMC)|(SLC)|(SALT LAKE)|(CITY)|(PROVO)|(OGDEN)|(ENDO )|( VALLEY)|( REGIONAL)|( CTR)|(GRANITE)|( INSTITUTE)|(INSTACARE)|(WASATCH)|(COUNTY)|(PEDIATRIC)|(CORP)|(CENTRAL)|(URGENT)|(CARE)|(UNIV)|(ODYSSEY)|(MOUNTAINSTAR)|( ORTHOPEDIC)|(INSTITUT)|(PARTNERSHIP)|(PHYSICIAN)|(CASTLEVIEW)|(CONSULTING)|(MAGEMENT)|(PRACTICE)|(EMERGENCY)|(SPECIALISTS)|(DIVISION)|(GUT WHISPERER)|(INTERMOUNTAIN)|(OBGYN)"
```

# Connect to GCP database
```{r}
bigrquery::bq_auth(path = 'D:/gcp_keys/healthcare-compare-prod-95b3b7349c32.json')

# set my project ID and dataset name
project_id <- 'healthcare-compare-prod'
dataset_name <- 'healthcare_compare'

con <- dbConnect(
  bigrquery::bigquery(),
  project = project_id,
  dataset = dataset_name,
  billing = project_id
)
```


# Get NPI table
```{r}
query <-  paste0("SELECT npi, clean_name, osa_group, osa_class, osa_specialization
                 FROM `healthcare-compare-prod.healthcare_compare.npi_full`")

#bq_project_query(billing, query) # uncomment to determine billing price for above query.

npi_full <- dbGetQuery(con, query) %>%
  data.table()
```


# get a subset of the NPI providers based upon taxonomy groups
```{r}
gs4_auth(email="alexnielson@utah.gov")
```


```{r}
surgery <- read_sheet("https://docs.google.com/spreadsheets/d/1GY8lKwUJuPHtpUl4EOw9eriLUDG9KkNWrMbaSnA5hOU/edit#gid=0",
                    sheet="major_surgery") %>% as.data.table
surgery <-  surgery[is.na(Remove) ] %>% .[["NUCC Classification"]]
```

```{r}
  npi_prov_pair <-  npi_full[osa_class %in% surgery] %>%
    .[,.(npi=npi,
         clean_name = clean_name
         )
      ]
```


# Load Data

```{r}
bun_proc <-  disk.frame("full_apcd.df")
```


# Birth
59610, 59612, 59614 - vbac delivery
59510, 59514, 59515 - cesarean delivery
59400, 59409, 59410 - Obstetrical care

omit:

d & c after delivery

```{r}
birth_vag <- bun_proc[surg_bun_t_obstetrical ==T & surg_bun_t_care==T]
birth_csec <- bun_proc[surg_bun_t_delivery==T & surg_bun_t_cesarean==T]
birth_vbac <- bun_proc[surg_bun_t_delivery==T & stri_detect_regex(surg_bun_descr,"vbac")==T]
```

## vaginal birth


```{r}
birth_vag <-  birth_vag[,`:=`(
  surg_sp_name_clean = surg_sp_npi %>% map_chr(get_npi_standard_name),
  surg_bp_name_clean = surg_bp_npi %>% map_chr(get_npi_standard_name),
  
  medi_sp_name_clean = medi_sp_npi %>% map_chr(get_npi_standard_name),
  medi_bp_name_clean = medi_bp_npi %>% map_chr(get_npi_standard_name),
  
  radi_sp_name_clean = radi_sp_npi %>% map_chr(get_npi_standard_name),
  radi_bp_name_clean = radi_bp_npi %>% map_chr(get_npi_standard_name),
  
  path_sp_name_clean = path_sp_npi %>% map_chr(get_npi_standard_name),
  path_bp_name_clean = path_bp_npi %>% map_chr(get_npi_standard_name),
  
  anes_sp_name_clean = anes_sp_npi %>% map_chr(get_npi_standard_name),
  anes_bp_name_clean = anes_bp_npi %>% map_chr(get_npi_standard_name),
  
  faci_sp_name_clean = faci_sp_npi %>% map_chr(get_npi_standard_name),
  faci_bp_name_clean = faci_bp_npi %>% map_chr(get_npi_standard_name)
  )]
```


```{r}
birth_vag %>% saveRDS("birth_vag.RDS")
```



```{r}
birth_vag <- birth_vag[cnt>5 & faci_bun_sum_med > 1000]
```


We will now examine the vaginal birth deliveries's median price distribution and cost correlated tags.

```{r}
birth_vag[cnt>5 & faci_bun_sum_med > 1000]%>% plot_med_density() %>% print()
birth_vag[cnt>5 & faci_bun_sum_med > 1000]%>% get_tag_cor() %>% print()
```


```{r}
birth_vag %>% get_tag_density_information("surg_bun_t_abdomen") %>% print()
```

There are only two with a exploratory abdomen surgery code, so we will omit them from the standard.
```{r}
birth_vag <- birth_vag[surg_bun_t_abdomen==F]
```


We will now examine the vaginal birth deliveries's median price distribution and cost correlated tags.

```{r}
birth_vag%>% plot_med_density() %>% print()
birth_vag%>% get_tag_cor() %>% print()
```

It now looks like the main differece has to do with the facility type. ie: 
Initial hospital care
Subsequent observation care
Subsequent hospital care
Emergency dept visit


```{r}
birth_vag %>% get_tag_density_information("faci_bun_t_initial") %>% print()
```

```{r}
birth_vag %>% get_tag_density_information("faci_bun_t_emergency") %>% print()
```

```{r}
birth_vag_init_hosp_care <- birth_vag[faci_bun_t_initial==T & faci_bun_t_hospital==T & faci_bun_t_care==T]
```

```{r}
birth_vag <- birth_vag[faci_bun_t_initial==F & faci_bun_t_hospital==F & faci_bun_t_care==F]
```

We will now examine the vaginal birth deliveries's median price distribution and cost correlated tags.

```{r}
birth_vag%>% plot_med_density() %>% print()
birth_vag%>% get_tag_cor() %>% print()
```


```{r}
birth_vag %>% get_tag_density_information("anes_bun_t_anes") %>% print()
```


```{r}
birth_vag <-  birth_vag[anes_bun_t_anes==T]
birth_bag_no_anes <- birth_vag[anes_bun_t_anes==F]
```

We will now examine the vaginal birth deliveries's median price distribution and cost correlated tags.

```{r}
birth_vag%>% plot_med_density() %>% print()
birth_vag%>% get_tag_cor() %>% print()
```


```{r}
birth_vag %>% get_tag_density_information("faci_bun_t_emergency") %>% print()
```


```{r}
birth_vag_w_anes_w_emerg_dept <- birth_vag[faci_bun_t_emergency==T & faci_bun_t_dept==T]
birth_vag <- birth_vag[faci_bun_t_emergency==F & faci_bun_t_dept==F]
```


We will now examine the vaginal birth deliveries's median price distribution and cost correlated tags.

```{r}
birth_vag%>% plot_med_density() %>% print()
birth_vag%>% get_tag_cor() %>% print()
```


```{r}
birth_vag %>% get_tag_density_information("surg_bun_t_hysterectomy") %>% print()
```

```{r}
birth_vag <- birth_vag[surg_bun_t_hysterectomy==F]
```


```{r}
birth_vag %>% get_tag_density_information("path_bun_t_tissue") %>% print()
```



We will now examine the vaginal birth deliveries's median price distribution and cost correlated tags.

```{r}
birth_vag%>% plot_med_density() %>% print()
birth_vag%>% get_tag_cor() %>% print()
```

```{r}
birth_vag %>% get_tag_density_information("path_bun_t_patho") %>% print()
```

```{r}
birth_vag_with_patho <- birth_vag[path_bun_t_patho==T]
birth_vag <- birth_vag[path_bun_t_patho==F]
```


We will now examine the vaginal birth deliveries's median price distribution and cost correlated tags.

```{r}
birth_vag %>% plot_med_density() %>% print()
birth_vag %>% get_tag_cor() %>% print()
```

```{r}
birth_vag[surg_bun_t_uterus==T] %>% nrow()
birth_vag %>% get_tag_density_information("path_bun_t_complete") %>% print()
birth_vag %>% get_tag_density_information("radi_bun_t_ct") %>% print()
```

```{r}
birth_vag <- birth_vag[surg_bun_t_uterus==F & path_bun_t_complete==F  & radi_bun_t_ct==F]
```

```{r}
birth_vag %>% plot_med_density() %>% print()
birth_vag %>% get_tag_cor() %>% print()
```

```{r}
birth_vag[cnt > 10 & faci_bun_sum_med > 2000] %>% plot_med_density() %>% print()
birth_vag[cnt > 10 & faci_bun_sum_med > 2000] %>% get_tag_cor() %>% print()
birth_vag[cnt > 10 & faci_bun_sum_med > 2000] %>% nrow()
```

```{r}
birth_vag <- birth_vag[cnt > 10 & faci_bun_sum_med > 2000]
```


```{r}
birth_vag %>% get_tag_density_information("medi_bun_t_clinic") %>% print()
```

```{r}
birth_vag <- birth_vag[medi_bun_t_clinic==F]
```


```{r}
birth_vag %>% plot_med_density() %>% print()
birth_vag %>% get_tag_cor() %>% print()
```

```{r}
birth_vag %>% get_tag_density_information("radi_bun_t_pelvi") %>% print()
```

```{r}
birth_vag <- birth_vag[radi_bun_t_pelvi==F]
```

```{r}
birth_vag %>% plot_med_density() %>% print()
birth_vag %>% get_tag_cor() %>% print()
```

```{r}
birth_vag[path_bun_t_fetal==T] %>% nrow()
```


```{r}
birth_vag <- birth_vag[path_bun_t_fetal==F]
```

```{r}
birth_vag %>% plot_med_density() %>% print()
birth_vag %>% get_tag_cor() %>% print()
```

## btb for vaginal births

```{r}
birth_vag_btbv4 <- birth_vag %>% btbv4()
```


```{r}
birth_vag_bq <- birth_vag_btbv4[,
                     primary_doctor := pmap(.l=list(doctor_npi1=doctor_npi_str1,
                                  doctor_npi2=doctor_npi_str2,
                                  class_reqs="Obstetrics & Gynecology"#,
                                  # specialization_reqs = "Obstetrics|||Maternal & Fetal Medicine"
                                  ),
                                                .f=calculate_primary_doctor) %>% as.character()
                     ] %>% 
  #Filter out any procedures where our doctors fail both criteria. 
  .[!(primary_doctor %in% c("BOTH_DOC_FAIL_CRIT", "TWO_FIT_ALL_SPECS"))] %>% 
  .[,primary_doctor_npi := fifelse(primary_doctor==doctor_str1,
                                   doctor_npi_str1,
                                   doctor_npi_str2)] %>% 
  .[,`:=`(procedure_type=5, procedure_modifier="Vaginal Delivery")]
```



```{r}
birth_vag_bq <- birth_vag_bq[,.(
primary_doctor,
primary_doctor_npi,
most_important_fac	,
most_important_fac_npi,	
procedure_type,
procedure_modifier,
tp_med_med,
tp_med_surg,
tp_med_medi,
tp_med_path,
tp_med_radi,
tp_med_anes,
tp_med_faci,
ingest_date = Sys.Date()
)]
```


```{r, eval=FALSE}
bq_table_upload(x=procedure_table, values= birth_vag_bq, create_disposition='CREATE_IF_NEEDED', write_disposition='WRITE_APPEND')
```


## birth_csec
```{r}
birth_csec %>% plot_med_density() %>% print()
birth_csec %>% get_tag_cor() %>% print()
```


```{r}
birth_csec <-  birth_csec[,`:=`(
  surg_sp_name_clean = surg_sp_npi %>% map_chr(get_npi_standard_name),
  surg_bp_name_clean = surg_bp_npi %>% map_chr(get_npi_standard_name),
  
  medi_sp_name_clean = medi_sp_npi %>% map_chr(get_npi_standard_name),
  medi_bp_name_clean = medi_bp_npi %>% map_chr(get_npi_standard_name),
  
  radi_sp_name_clean = radi_sp_npi %>% map_chr(get_npi_standard_name),
  radi_bp_name_clean = radi_bp_npi %>% map_chr(get_npi_standard_name),
  
  path_sp_name_clean = path_sp_npi %>% map_chr(get_npi_standard_name),
  path_bp_name_clean = path_bp_npi %>% map_chr(get_npi_standard_name),
  
  anes_sp_name_clean = anes_sp_npi %>% map_chr(get_npi_standard_name),
  anes_bp_name_clean = anes_bp_npi %>% map_chr(get_npi_standard_name),
  
  faci_sp_name_clean = faci_sp_npi %>% map_chr(get_npi_standard_name),
  faci_bp_name_clean = faci_bp_npi %>% map_chr(get_npi_standard_name)
  )]
```

```{r}
birth_csec %>% saveRDS("birth_csec.RDS")
```

```{r}
birth_csec <- readRDS("birth_csec.RDS")
```


```{r}
birth_csec[cnt>5 & faci_bun_sum_med > 3000 & tp_med < 60000] %>% plot_med_density() %>% print()
birth_csec[cnt>5 & faci_bun_sum_med > 3000 & tp_med < 60000] %>% get_tag_cor() %>% print()
```

```{r}
birth_csec <- birth_csec[cnt>5 & faci_bun_sum_med > 3000 & tp_med < 60000]
```


```{r}
birth_csec %>% plot_med_density() %>% print()
birth_csec %>% get_tag_cor() %>% print()
```

```{r}
birth_csec %>% get_tag_density_information("faci_bun_t_initial") %>% print()
```

Statiscally significant different groups, but too small to represent own group. 


```{r}
birth_csec <- birth_csec[faci_bun_t_initial==F]
```

Now, we wil recheck the median price density and highly correlated tags.
```{r}
birth_csec %>% plot_med_density() %>% print()
birth_csec %>% get_tag_cor() %>% print()
```

```{r}
birth_csec %>% get_tag_density_information("faci_bun_t_emergency") %>% print()
```

```{r}
birth_csec <- birth_csec[faci_bun_t_emergency == F  & faci_bun_t_discharge == F]

```

ow, we wil recheck the median price density and highly correlated tags.
```{r}
birth_csec %>% plot_med_density() %>% print()
birth_csec %>% get_tag_cor() %>% print()
```

```{r}
birth_csec %>% get_tag_density_information("anes_bun_t_vag") %>% print()
```

```{r}
birth_csec_w_anes <- birth_csec[anes_bun_t_vag==T]
birth_csec_n_anes <- birth_csec[anes_bun_t_vag==F]
```

## birth_csec_n_anes
```{r}
birth_csec_n_anes %>% plot_med_density() %>% print()
birth_csec_n_anes %>% get_tag_cor() %>% print()
```

## birth_csec_w_anes

we will now look at the density distribution for csection births with anesthesia
```{r}
birth_csec_w_anes %>% plot_med_density() %>% print()
birth_csec_w_anes %>% get_tag_cor() %>% print()
```

```{r}
birth_csec_w_anes[surg_bun_t_remove==T] %>% nrow()
```
only one in with that tag
```{r}
birth_csec_w_anes <- birth_csec_w_anes[surg_bun_t_remove==F]
```

```{r}
birth_csec_w_anes[surg_bun_t_ovarian==T] %>% nrow()
```
only one in with that tag
```{r}
birth_csec_w_anes <- birth_csec_w_anes[surg_bun_t_ovarian==F]
```


we will now look at the density distribution for csection births with anesthesia
```{r}
birth_csec_w_anes %>% plot_med_density() %>% print()
birth_csec_w_anes %>% get_tag_cor() %>% print()
```


```{r}
birth_csec %>% get_tag_density_information("radi_bun_t_artery") %>% print()
```

```{r}
birth_csec_w_anes <- birth_csec_w_anes[radi_bun_t_artery==F]
```


we will now look at the density distribution for csection births with anesthesia
```{r}
birth_csec_w_anes %>% plot_med_density() %>% print()
birth_csec_w_anes %>% get_tag_cor() %>% print()
```


```{r}
birth_csec_w_anes %>% get_tag_density_information("faci_bun_t_hospital") %>% print()
```


```{r}
birth_csec_w_anes_w_sub_hosp_care <- birth_csec_w_anes[faci_bun_t_care==T & faci_bun_t_subsequent ==T]
birth_csec_w_anes <- birth_csec_w_anes[faci_bun_t_care==F & faci_bun_t_subsequent ==F]
```



we will now look at the density distribution for csection births with anesthesia
```{r}
birth_csec_w_anes %>% plot_med_density() %>% print()
birth_csec_w_anes %>% get_tag_cor() %>% print()
```

```{r}
birth_csec_w_anes %>% get_tag_density_information("path_bun_t_complete") %>% print()
birth_csec_w_anes[path_bun_t_colon==T] %>% nrow()
birth_csec_w_anes[surg_bun_t_abdom==T] %>% nrow()
```

There is weak evidence to split, but since only 19 of them are listed a complete pathology panel, I will omit the 19. This also gets rid of a few outliers. 



```{r}
birth_csec_w_anes <- birth_csec_w_anes[path_bun_t_complete==F & path_bun_t_colon==F & surg_bun_t_abdom==F]
```

we will now look at the density distribution for csection births with anesthesia
```{r}
birth_csec_w_anes %>% plot_med_density() %>% print()
birth_csec_w_anes %>% get_tag_cor() %>% print()
```

```{r}
birth_csec_w_anes %>% get_tag_density_information("surg_bun_t_exc") %>% print()
```
Small subset and not a standard procedure based on frequency. 


```{r}
birth_csec_w_anes <- birth_csec_w_anes[surg_bun_t_exc==F]
```

we will now look at the density distribution for csection births with anesthesia
```{r}
birth_csec_w_anes %>% plot_med_density() %>% print()
birth_csec_w_anes %>% get_tag_cor() %>% print()
```


```{r}
birth_csec_w_anes[surg_bun_t_injection==T] %>% nrow()
birth_csec_w_anes[path_bun_t_amniotic==T] %>% nrow()
birth_csec_w_anes[surg_bun_t_antepartum==T] %>% nrow()
birth_csec_w_anes[surg_bun_t_perineum==T] %>% nrow()
```

```{r}
birth_csec_w_anes <- birth_csec_w_anes[surg_bun_t_injection==F & path_bun_t_amniotic==F & surg_bun_t_perineum==F]
```


we will now look at the density distribution for csection births with anesthesia
```{r}
birth_csec_w_anes %>% plot_med_density() %>% print()
birth_csec_w_anes %>% get_tag_cor() %>% print()
```


```{r}
birth_csec_w_anes <- birth_csec_w_anes[ tp_med > 6000]
```



```{r}
birth_csec_w_anes_btbv4 <- birth_csec_w_anes %>% btbv4()
```

```{r}
birth_csec_w_anes_bq <- birth_csec_w_anes_btbv4[,
                     primary_doctor := pmap(.l=list(doctor_npi1=doctor_npi_str1,
                                  doctor_npi2=doctor_npi_str2,
                                  class_reqs="Obstetrics & Gynecology",
                                  specialization_reqs = "Obstetrics|||Maternal & Fetal Medicine"
                                  ),
                                                .f=calculate_primary_doctor)
                     ] %>% 
  #Filter out any procedures where our doctors fail both criteria. 
  .[!(primary_doctor %in% c("BOTH_DOC_FAIL_CRIT", "TWO_FIT_ALL_SPECS", "NONE_FIT_SPEC_REQ"))] %>% 
  .[,primary_doctor_npi := fifelse(primary_doctor==doctor_str1,
                                   doctor_npi_str1,
                                   doctor_npi_str2)] %>% 
  .[,`:=`(procedure_type=4, procedure_modifier="Caesarean Delivery")]
```


##birth_csec_w_anes_w_sub_hosp_care


we will now look at the density distribution for csection births with anesthesia that also had subsequent hospital care
```{r}
birth_csec_w_anes_w_sub_hosp_care %>% plot_med_density() %>% print()
birth_csec_w_anes_w_sub_hosp_care %>% get_tag_cor() %>% print()
```

```{r}
birth_csec_w_anes_w_sub_hosp_care <- birth_csec_w_anes_w_sub_hosp_care[ tp_med > 6000]
```

```{r}
birth_csec_w_anes_w_sub_hosp_care_btbv4 <- birth_csec_w_anes_w_sub_hosp_care %>% btbv4()
```



```{r}
birth_csec_w_anes_w_sub_hosp_care_bq <- birth_csec_w_anes_w_sub_hosp_care_btbv4[,
                     primary_doctor := pmap(.l=list(doctor_npi1=doctor_npi_str1,
                                  doctor_npi2=doctor_npi_str2,
                                  class_reqs="Obstetrics & Gynecology",
                                  specialization_reqs = "Obstetrics|||Maternal & Fetal Medicine"
                                  ),
                                                .f=calculate_primary_doctor) %>% as.character()
                     ] %>% 
  #Filter out any procedures where our doctors fail both criteria. 
  .[!(primary_doctor %in% c("BOTH_DOC_FAIL_CRIT", "TWO_FIT_ALL_SPECS", "NONE_FIT_SPEC_REQ"))] %>% 
  .[,primary_doctor_npi := fifelse(primary_doctor==doctor_str1,
                                   doctor_npi_str1,
                                   doctor_npi_str2)] %>% 
  .[,`:=`(procedure_type=5, procedure_modifier="Caesarean Delivery with Subsequent Hospital Care")]
```



```{r}
birth_csec_w_anes_w_sub_hosp_care_bq <- birth_csec_w_anes_w_sub_hosp_care_bq[,.(
primary_doctor,
primary_doctor_npi,
most_important_fac	,
most_important_fac_npi,	
procedure_type,
procedure_modifier,
tp_med_med,
tp_med_surg,
tp_med_medi,
tp_med_path,
tp_med_radi,
tp_med_anes,
tp_med_faci,
ingest_date = Sys.Date()
)]
```

```{r, eval=FALSE}
bq_table_upload(x=procedure_table, values= birth_csec_w_anes_w_sub_hosp_care_bq, create_disposition='CREATE_IF_NEEDED', write_disposition='WRITE_APPEND')
```




<!-- ## vbac birth -->

<!-- ```{r} -->
<!-- birth_vbac <-  birth_vbac[,`:=`( -->
<!--   surg_sp_name_clean = surg_sp_npi %>% map_chr(get_npi_standard_name), -->
<!--   surg_bp_name_clean = surg_bp_npi %>% map_chr(get_npi_standard_name), -->

<!--   medi_sp_name_clean = medi_sp_npi %>% map_chr(get_npi_standard_name), -->
<!--   medi_bp_name_clean = medi_bp_npi %>% map_chr(get_npi_standard_name), -->

<!--   radi_sp_name_clean = radi_sp_npi %>% map_chr(get_npi_standard_name), -->
<!--   radi_bp_name_clean = radi_bp_npi %>% map_chr(get_npi_standard_name), -->

<!--   path_sp_name_clean = path_sp_npi %>% map_chr(get_npi_standard_name), -->
<!--   path_bp_name_clean = path_bp_npi %>% map_chr(get_npi_standard_name), -->

<!--   anes_sp_name_clean = anes_sp_npi %>% map_chr(get_npi_standard_name), -->
<!--   anes_bp_name_clean = anes_bp_npi %>% map_chr(get_npi_standard_name), -->

<!--   faci_sp_name_clean = faci_sp_npi %>% map_chr(get_npi_standard_name), -->
<!--   faci_bp_name_clean = faci_bp_npi %>% map_chr(get_npi_standard_name) -->
<!--   )] -->
<!-- ``` -->

<!-- ```{r} -->
<!-- birth_vbac %>% saveRDS("birth_vbac.RDS") -->
<!-- ``` -->

<!-- ```{r} -->
<!-- birth_vbac <- readRDS("birth_vbac.RDS") -->
<!-- ``` -->


<!-- ```{r} -->
<!-- birth_vbac[cnt > 5] %>% plot_med_density() %>% print() -->
<!-- birth_vbac[cnt > 5] %>% get_tag_cor() %>% print() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- birth_vbac %>% get_tag_density_information("anes_bun_t_cs") %>% print() -->
<!-- ``` -->



<!-- I am not going to do these ones right now. IF we end up wanting VBAC i will add it in later.  -->
