---
title: Colonoscopy
author: Alexander Nielson
date: '2020-07-31'
slug: colonoscopy
categories:
  - Major Surgery
tags:
  - Colonoscopy
  - Biopsy
  - Surgery
keywords:
  - tech
---

# Introduction

In this section we will:  
* identify which colonoscopy procedures were excluded and why
* identify which different colonoscopy subgroups were created and why


If you have questions or concerns about this data please contact Alexander Nielson (alexnielson@utah.gov) 


# Load Libraries
Load Libraries
```{r, message=FALSE}
library(data.table)
library(tidyverse)
library(stringi)
library(ggridges)
library(broom)
library(disk.frame)
library(RecordLinkage)
library(googlesheets4)
library(bigrquery)
library(DBI)
devtools::install_github("utah-osa/hcctools2", upgrade="never" )
library(hcctools2)
```

Establish color palettes

```{r}
cust_color_pal1 <- c(
        "Anesthesia" = "#f3476f",
        "Facility" = "#e86a33",
        "Medicine Proc" = "#e0a426",
        "Pathology" = "#77bf45",
        "Radiology" = "#617ff7",
        "Surgery" = "#a974ee"
    )

cust_color_pal2 <- c(
        "TRUE" = "#617ff7",
        "FALSE" = "#e0a426"
    )

cust_color_pal3 <- c(
        "above avg" = "#f3476f",
        "avg" = "#77bf45",
        "below avg" = "#a974ee"
    )



  fac_ref_regex <- "(UTAH)|(IHC)|(HOSP)|(HOSPITAL)|(CLINIC)|(ANESTH)|(SCOPY)|(SURG)|(LLC)|(ASSOC)|(MEDIC)|(CENTER)|(ASSOCIATES)|(U OF U)|(HEALTH)|(OLOGY)|(OSCOPY)|(FAMILY)|(VAMC)|(SLC)|(SALT LAKE)|(CITY)|(PROVO)|(OGDEN)|(ENDO )|( VALLEY)|( REGIONAL)|( CTR)|(GRANITE)|( INSTITUTE)|(INSTACARE)|(WASATCH)|(COUNTY)|(PEDIATRIC)|(CORP)|(CENTRAL)|(URGENT)|(CARE)|(UNIV)|(ODYSSEY)|(MOUNTAINSTAR)|( ORTHOPEDIC)|(INSTITUT)|(PARTNERSHIP)|(PHYSICIAN)|(CASTLEVIEW)|(CONSULTING)|(MAGEMENT)|(PRACTICE)|(EMERGENCY)|(SPECIALISTS)|(DIVISION)|(GUT WHISPERER)|(INTERMOUNTAIN)|(OBGYN)"
```

# Connect to GCP database
```{r}
bigrquery::bq_auth(path = 'D:/gcp_keys/healthcare-compare-prod-95b3b7349c32.json')

# set my project ID and dataset name
project_id <- 'healthcare-compare-prod'
dataset_name <- 'healthcare_compare'

con <- dbConnect(
  bigrquery::bigquery(),
  project = project_id,
  dataset = dataset_name,
  billing = project_id
)
```


# Get NPI table
```{r}
query <-  paste0("SELECT npi, clean_name, osa_group, osa_class, osa_specialization
                 FROM `healthcare-compare-prod.healthcare_compare.npi_full`")
                       
#bq_project_query(billing, query) # uncomment to determine billing price for above query.

npi_full <- dbGetQuery(con, query) %>%
  data.table() 
```


# get a subset of the NPI providers based upon taxonomy groups
```{r}
gs4_auth(email="alexnielson@utah.gov")
```


```{r}
surgery <- read_sheet("https://docs.google.com/spreadsheets/d/1GY8lKwUJuPHtpUl4EOw9eriLUDG9KkNWrMbaSnA5hOU/edit#gid=0",
                    sheet="major_surgery") %>% as.data.table
surgery <-  surgery[is.na(Remove) ] %>% .[["NUCC Classification"]]
```

```{r}
  npi_prov_pair <-  npi_full[osa_class %in% surgery] %>% 
    .[,.(npi=npi,
         clean_name = clean_name
         )
      ] 
```


# Load Data

```{r}
bun_proc <-  disk.frame("full_apcd.df")
```



```{r}
cscopy <- bun_proc[surg_bun_t_colonoscopy == T & cnt >5 & tp_med < 10000]
```


```{r}
cscopy <-  cscopy[,`:=`(
  surg_sp_name_clean = surg_sp_npi %>% map_chr(get_npi_standard_name),
  surg_bp_name_clean = surg_bp_npi %>% map_chr(get_npi_standard_name),
  
  medi_sp_name_clean = medi_sp_npi %>% map_chr(get_npi_standard_name),
  medi_bp_name_clean = medi_bp_npi %>% map_chr(get_npi_standard_name),
  
  radi_sp_name_clean = radi_sp_npi %>% map_chr(get_npi_standard_name),
  radi_bp_name_clean = radi_bp_npi %>% map_chr(get_npi_standard_name),
  
  path_sp_name_clean = path_sp_npi %>% map_chr(get_npi_standard_name),
  path_bp_name_clean = path_bp_npi %>% map_chr(get_npi_standard_name),
  
  anes_sp_name_clean = anes_sp_npi %>% map_chr(get_npi_standard_name),
  anes_bp_name_clean = anes_bp_npi %>% map_chr(get_npi_standard_name),
  
  faci_sp_name_clean = faci_sp_npi %>% map_chr(get_npi_standard_name),
  faci_bp_name_clean = faci_bp_npi %>% map_chr(get_npi_standard_name)
                           )]
```


```{r}
cscopy %>% saveRDS("cscopy.RDS")
```

```{r}
cscopy <- readRDS("cscopy.RDS")
```


anything under 600 is  known to be too low. while some clinics may perform colonoscopies at a lower rate, a 600 dolar charge is not typical. 

```{r}
cscopy <- cscopy[tp_med > 600 & tp_med < 10000]
```


```{r}
cscopy[,tp_med] %>% summary()
```

## A. Standard

We want to find the typical/standard colonoscopy. To do this we need to split and filter out the procedures that we would not typically think as a standard colonoscopy. These groups may be valid and deserve their own category, or they may be rare procedure types which we do not believe the average customer is shopping for. 


```{r}
cscopy %>% plot_med_density() %>% print()
cscopy %>% get_tag_cor() %>% print()
```

lets compare the procedures which have an EGD and a colonoscopy

```{r}
cscopy %>% get_tag_density_information(tag="surg_bun_t_egd") %>% print()
```

these are clearly different. If a patient has an EGD and a colonoscopy, they are being charged much more than if there was no EGD. 


```{r}
cscopy_with_egd <- cscopy[surg_bun_t_egd ==T]
cscopy <- cscopy[surg_bun_t_egd ==F]
```

Lets now once again examine the distribution and examine any correlated tags

```{r}
cscopy %>% plot_med_density() %>% print()
cscopy %>% get_tag_cor() %>% print()
```

now lets examine the colonoscopies with lesion removal 
```{r}
cscopy %>% get_tag_density_information(tag="surg_bun_t_lesion") %>% print()
```
There is strong evidence to remove split these procedures into separate groups. While the Doctor and/or patient may not know if a lesion will be removed prior to surgery, there is a price difference. This will help with post procedure customer analyis. 

```{r}
cscopy_with_lesion <- cscopy[surg_bun_t_lesion ==T]
cscopy <- cscopy[surg_bun_t_lesion ==F]
```

check distribution and correlated tags
```{r}
cscopy %>% plot_med_density() %>% print()
cscopy %>% get_tag_cor() %>% print()
```

```{r}
cscopy %>% get_tag_density_information("medi_bun_t_inject") %>% print()
```

weak evidence to split based on injection, so for now we will not split. Lets check the tissue pathology next



```{r}
cscopy %>% get_tag_density_information(tag="path_bun_t_tissue") %>% print()
```

There is strong evidence to split based upon whether a tissue pathology was conducted. This also passes a gut check since if a tissue had a pathology procedure that it would have cost more to the patient. 

```{r}
cscopy_with_tissue<- cscopy[path_bun_t_tissue ==T]
cscopy <- cscopy[path_bun_t_tissue ==F]
```


```{r}
cscopy %>% plot_med_density() %>% print()
cscopy %>% get_tag_cor() %>% print()
```

lets check for colonoscopies at the emergency department

```{r}
cscopy %>% get_tag_density_information(tag="faci_bun_t_emergency") %>% print()
```
There is strong evidence that a colonoscopy at the emergency department costs much more than one not at an emergency department, however the frequency is not high, so it will not be a serparate searchable category. 

```{r}
cscopy_at_emerg <-  cscopy[faci_bun_t_emergency==T]
cscopy <-  cscopy[faci_bun_t_emergency==F]
```



```{r}
cscopy %>% plot_med_density() %>% print()
cscopy %>% get_tag_cor() %>% print()
```
lets remove some obviously non standard additional procedures
```{r}
cscopy <- cscopy[surg_bun_t_anal==F & surg_bun_t_finger==F & anes_bun_t_hernia==F & surg_bun_t_pharynx==F & surg_bun_t_hernia ==F & surg_bun_t_anal==F & surg_bun_t_lap==F ]
```


```{r}
cscopy %>% plot_med_density() %>% print()
```
We are now happy with this distribution and values for the standard colonoscopy. 
Now we will group the bundles by the facility, and doctor pairs based upon the NPI database. 
```{r}
cscopy_btbv4 <-  cscopy %>% btbv4()
```

For colonoscopies, we will only show those which performed at least 25 surgeries. 
```{r}
cscopy_btbv4 <- cscopy_btbv4 %>% 
 arrange(most_important_fac) %>% 
  filter(tp_cnt_cnt>9) %>%
  select(doctor_str1,
         doctor_str2,
         doctor_npi_str1,
         doctor_npi_str2,
         most_important_fac,
         most_important_fac_npi,
         tp_med_med,
         tp_med_surg,
         tp_med_medi,
         tp_med_path,
         tp_med_radi,
         tp_med_anes,
         tp_med_faci,
         tp_cnt_cnt) %>%
  mutate(procedure_type = 1,
         procedure_modifier = "Standard")

```

```{r}
cscopy_btbv4 %>% as.data.frame()%>% count(doctor_str1,doctor_str2, most_important_fac) %>% filter(n>1)
```


## B. EGD 

```{r}
cscopy_with_egd %>% plot_med_density() %>% print()
```


```{r}
cscopy_with_egd %>% get_tag_cor() %>% print()
```

```{r}
cscopy_with_egd %>% get_tag_density_information("medi_bun_t_sodium") %>% print()
```

```{r}
cscopy_with_edg_with_sodium <-  cscopy_with_egd[medi_bun_t_sodium==T]
cscopy_with_egd <- cscopy_with_egd[medi_bun_t_sodium==F]
```

```{r}
cscopy_with_egd %>% get_tag_cor() %>% print()
```

## C. Lesion Removal 
We will now break down the Colonoscopy with Lesion Removal Category down into appropriate categories. 

lets check the dist and correlated tags
```{r}
cscopy_with_lesion %>% plot_med_density() %>% print()
cscopy_with_lesion %>% get_tag_cor() %>% print()
```



```{r}
cscopy_with_lesion %>% get_tag_density_information("medi_bun_t_inject") %>% print()
```
we have strong evidence to create a new group for cscopy with a lesion removal with an injection.


```{r}
cscopy_with_lesion_with_injection <- cscopy_with_lesion[medi_bun_t_inject==T]
cscopy_with_lesion <-  cscopy_with_lesion[medi_bun_t_inject==F]
```


lets check the dist and correlated tags
```{r}
cscopy_with_lesion %>% plot_med_density() %>% print()
cscopy_with_lesion %>% get_tag_cor() %>% print()
```

```{r}
cscopy_with_lesion %>% get_tag_density_information("surg_bun_t_biopsy") %>% print()
```
There is strong evidence that a lesion removal with a biopsy should be a separate procedure.


```{r}
cscopy_with_lesion_and_biopsy <- cscopy_with_lesion[surg_bun_t_biopsy==T]
cscopy_with_lesion <-  cscopy_with_lesion[surg_bun_t_biopsy==F]
```

lets check the dist and correlated tags
```{r}
cscopy_with_lesion %>% plot_med_density() %>% print()
cscopy_with_lesion %>% get_tag_cor() %>% print()
```

the njx tag is picking up is "Egd us transmural injxn/mark" or "Colonoscopy submucous njx"

```{r}
cscopy_with_lesion %>% get_tag_density_information("surg_bun_t_sub") %>% print()
```
while there is a legitimate difference, it is not a large enough sample to warrant a separate procedure options

```{r}
cscopy_with_lesion <-  cscopy_with_lesion[surg_bun_t_sub==F]
```

lets check the dist and correlated tags
```{r}
cscopy_with_lesion %>% plot_med_density() %>% print()
cscopy_with_lesion %>% get_tag_cor() %>% print()
```

```{r}
cscopy_with_lesion %>% get_tag_density_information("faci_bun_t_emergency") %>% print()
```
not a large enough sample to warrant a split. 

```{r}
cscopy_with_lesion <- cscopy_with_lesion[faci_bun_t_emergency==F]
```

lets check the dist and correlated tags
```{r}
cscopy_with_lesion %>% plot_med_density() %>% print()
cscopy_with_lesion %>% get_tag_cor() %>% print()
```

```{r}
cscopy_with_lesion <- cscopy_with_lesion[surg_bun_t_sheath==F & surg_bun_t_block==F & surg_bun_t_eye==F & surg_bun_t_cystoscopy==F]
```


```{r}
cscopy_with_lesion  %>% get_tag_density_information("path_bun_t_patho") %>% print()
```
Not justified to split

lets check the dist and correlated tags
```{r}
cscopy_with_lesion %>% plot_med_density() %>% print()
cscopy_with_lesion %>% get_tag_cor() %>% print()
```

```{r}
cscopy_with_lesion_btbv4 <- cscopy_with_lesion %>% btbv4()
```

```{r}
cscopy_with_lesion_btbv4 <- cscopy_with_lesion_btbv4 %>% 
  filter(tp_cnt_cnt>5) %>% 
  select(doctor_str1,
         doctor_str2,
         doctor_npi_str1,
         doctor_npi_str2,
         most_important_fac,
         most_important_fac_npi,
         tp_med_med,
         tp_med_surg,
         tp_med_medi,
         tp_med_path,
         tp_med_radi,
         tp_med_anes,
         tp_med_faci,
         tp_cnt_cnt) %>%
  mutate(procedure_type = 1,
         procedure_modifier = "Lesion Removal")

cscopy_with_lesion_btbv4
```

### 1. injection
lets break down the lesion removal with an injection
```{r}
cscopy_with_lesion_with_injection %>% get_tag_cor() %>% print()
cscopy_with_lesion_with_injection %>% plot_med_density() %>% print()
```

```{r}
cscopy_with_lesion_with_injection %>% get_tag_density_information("surg_bun_t_sub") %>% print()
```

```{r}
cscopy_with_lesion_with_injection <-  cscopy_with_lesion_with_injection[surg_bun_t_sub==F]
```

```{r}
cscopy_with_lesion_with_injection %>% get_tag_density_information("surg_bun_t_biopsy") %>% print()
```

```{r}
cscopy_with_lesion_biopsy_injection <- cscopy_with_lesion_with_injection[surg_bun_t_biopsy==T]
cscopy_with_lesion_with_injection <- cscopy_with_lesion_with_injection[surg_bun_t_biopsy==F]
```


```{r}
cscopy_with_lesion_with_injection %>%  get_tag_cor() %>% print()
```


```{r}
cscopy_with_lesion_with_injection %>% get_tag_density_information("surg_bun_t_remove") %>% print()
```

```{r}
cscopy_with_lesion_with_injection <- cscopy_with_lesion_with_injection[surg_bun_t_resect==F & surg_bun_t_remove==F & medi_bun_t_normal==F ]
```


```{r}
cscopy_with_lesion_with_injection %>% plot_med_density() %>% print()
```

```{r}
cscopy_with_lesion_with_injection_bundle <-  cscopy_with_lesion_with_injection %>% btbv4()
```

```{r}
# cscopy_with_lesion_with_injection_bundle %>% View()
```

```{r}
# cscopy_with_lesion_with_injection_bundle %>% saveRDS("dash_colonoscopy_lesion_injection.RDS")
```


### 2. biopsy
```{r}
cscopy_with_lesion_and_biopsy %>% get_tag_cor() %>% print()
cscopy_with_lesion_and_biopsy %>% plot_med_density() %>% print()
```


```{r}
cscopy_with_lesion_and_biopsy %>% get_tag_density_information("surg_bun_t_njx") %>% print()
```

```{r}
cscopy_with_lesion_and_biopsy <- cscopy_with_lesion_and_biopsy[surg_bun_t_njx==F & surg_bun_t_sub==F]
```


```{r}
cscopy_with_lesion_and_biopsy %>% get_tag_density_information("path_bun_t_patho") %>% print()
```


```{r}
cscopy_with_lesion_and_biopsy <-  cscopy_with_lesion_and_biopsy[path_bun_t_patho==T]
```

```{r}
cscopy_with_lesion_and_biopsy <- cscopy_with_lesion_and_biopsy[path_bun_t_metabolic==F & faci_bun_t_emergency==F]
```


```{r}
cscopy_with_lesion_and_biopsy %>% get_tag_cor() %>% print()
cscopy_with_lesion_and_biopsy %>% plot_med_density() %>% print()
```

```{r}
cscopy_with_lesion_and_biopsy %>% get_tag_density_information("anes_bun_t_mod_sed") %>% print()
```
there is strong evidence to split those groups into two. 

```{r}
cscopy_with_lesion_and_biopsy_and_mod_sed <-  cscopy_with_lesion_and_biopsy[anes_bun_t_mod_sed==T]
cscopy_with_lesion_and_biopsy <- cscopy_with_lesion_and_biopsy[anes_bun_t_mod_sed==F]
```

lets check the dist and correlated tags
```{r}
cscopy_with_lesion_and_biopsy %>% get_tag_cor() %>% print()
cscopy_with_lesion_and_biopsy %>% plot_med_density() %>% print()
```

```{r}
cscopy_with_lesion_and_biopsy <-  cscopy_with_lesion_and_biopsy[surg_bun_t_resect==F & path_bun_t_immuno==F & path_bun_t_hormone==F & path_bun_t_sex==F & surg_bun_t_breast==F]
```


```{r}
cscopy_with_lesion_and_biopsy2 <- cscopy_with_lesion_and_biopsy
```


```{r}
cscopy_with_lesion_and_biopsy_btbv4 <- cscopy_with_lesion_and_biopsy %>% btbv4()
```

```{r}
cscopy_with_lesion_and_biopsy_btbv4 <- cscopy_with_lesion_and_biopsy_btbv4 %>% 
  filter(tp_cnt_cnt>5) %>%
  arrange(most_important_fac) %>% 
  select(doctor_str1,
         doctor_str2,
         doctor_npi_str1,
         doctor_npi_str2,
         most_important_fac,
         most_important_fac_npi,
         tp_med_med,
         tp_med_surg,
         tp_med_medi,
         tp_med_path,
         tp_med_radi,
         tp_med_anes,
         tp_med_faci,
         tp_cnt_cnt) %>% 
  mutate(procedure_type = 1,
         procedure_modifier = "Lesion Removal AND Biopsy")
cscopy_with_lesion_and_biopsy_btbv4
```



### 3. Even more break downs.
While these are valid break downs, they seems to complex for the average customer to shop for, so I am going to display them, but they will not be in the final tool.

```{r}
cscopy_with_lesion_biopsy_injection %>% get_tag_cor() %>% print()
cscopy_with_lesion_biopsy_injection %>% plot_med_density() %>% print()
```

```{r}
cscopy_with_lesion_biopsy_injection %>% get_tag_density_information("anes_bun_t_mod_sed") %>% print()
```
```{r}
cscopy_with_lesion_biopsy_injection <-  cscopy_with_lesion_biopsy_injection[surg_bun_t_resect==F] 
```


```{r}
cscopy_with_lesion_biopsy_injection_mod_sed <-  cscopy_with_lesion_biopsy_injection[anes_bun_t_mod_sed==T]

cscopy_with_lesion_biopsy_injection <- cscopy_with_lesion_biopsy_injection[anes_bun_t_mod_sed==F]
```

```{r}
cscopy_with_lesion_biopsy_injection %>% get_tag_cor() %>% print()
cscopy_with_lesion_biopsy_injection %>% plot_med_density() %>% print()
```

```{r}
cscopy_with_lesion_biopsy_injection_mod_sed %>% get_tag_cor() %>% print()
cscopy_with_lesion_biopsy_injection_mod_sed %>% plot_med_density() %>% print()
```

## D. Tissue pathology
I will now break down the Colonoscopy with a tissue pathology

lets look at the distribution and correlated tags
```{r}
cscopy_with_tissue %>% plot_med_density() %>% print()
cscopy_with_tissue %>% get_tag_cor() %>% print()
```

```{r}
cscopy_with_tissue %>% get_tag_density_information("anes_bun_t_anesth") %>% print()
```
valid split, but not a large enough grouping to warrant own category. 

```{r}
cscopy_with_tissue  <- cscopy_with_tissue[anes_bun_t_anesth == F]
```

lets look at the distribution and correlated tags
```{r}
cscopy_with_tissue %>% plot_med_density() %>% print()
cscopy_with_tissue %>% get_tag_cor() %>% print()
```

```{r}
cscopy_with_tissue %>% get_tag_density_information("anes_bun_t_mod_sed") %>% print()
```

```{r}
cscopy_with_tissue_with_mod_sed <-  cscopy_with_tissue[anes_bun_t_mod_sed == T]
cscopy_with_tissue <- cscopy_with_tissue[anes_bun_t_mod_sed == F]
```


```{r}
cscopy_with_tissue %>% plot_med_density() %>% print()
cscopy_with_tissue %>% get_tag_cor() %>% print()
```

```{r}
cscopy_with_tissue %>% get_tag_density_information("faci_bun_t_hospital") %>% print()
```
```{r}
cscopy_with_tissue <-  cscopy_with_tissue[faci_bun_t_initial==F & medi_bun_t_normal==F & faci_bun_t_discharge==F & faci_bun_t_emergency==F & faci_bun_t_hospital==F & medi_bun_t_sodium==F & surg_bun_t_resect==F & path_bun_t_panel==F & surg_bun_t_anal==F & surg_bun_t_destroy==F & medi_bun_t_wheezing==F & surg_bun_t_nasal == F & path_bun_t_hiv==F & path_bun_t_allerg==F & path_bun_t_pregnancy==F & surg_bun_t_dilat==F]
```

```{r}
cscopy_with_tissue %>% plot_med_density() %>% print()
cscopy_with_tissue %>% get_tag_cor() %>% print()
```

```{r}
cscopy_with_tissue_btbv4 <- cscopy_with_tissue %>% btbv4()
```

```{r}
cscopy_with_tissue_btbv4 <- cscopy_with_tissue_btbv4 %>% 
  filter(tp_cnt_cnt>5) %>%
  arrange(most_important_fac) %>% 
  select(doctor_str1,
         doctor_str2,
         doctor_npi_str1,
         doctor_npi_str2,
         most_important_fac,
         most_important_fac_npi,
         tp_med_med,
         tp_med_surg,
         tp_med_medi,
         tp_med_path,
         tp_med_radi,
         tp_med_anes,
         tp_med_faci,
         tp_cnt_cnt) %>% 
  mutate(procedure_type = 1,
         procedure_modifier = "Tissue Pathology")
cscopy_with_tissue_btbv4
```


```{r}
cscopy_final <- cscopy_btbv4 %>%
  rbind(cscopy_with_lesion_btbv4) %>%
  rbind(cscopy_with_lesion_and_biopsy_btbv4) %>% 
  rbind(cscopy_with_tissue_btbv4)
```



```{r}
cscopy_final %>% saveRDS("cscopy_final.RDS")
```


```{r}
cscopy_final %>% nrow()
cscopy_final %>% count(doctor_str2) %>% arrange(desc(n))
```
946 bundles.
71 rows





```{r}
cscopy_final_bq <- cscopy_final[,
                     primary_doctor := pmap(.l=list(doctor_npi1=doctor_npi_str1,
                                  doctor_npi2=doctor_npi_str2,
                                  class_reqs="Internal Medicine|||Colon & Rectal Surgery",
                                  specialization_reqs="Gastroenterology"),
                                                .f=calculate_primary_doctor) %>% as.character()
                     ] %>% 
  #Filter out any procedures where our doctors fail both criteria. 
  .[!(primary_doctor %in% c("BOTH_DOC_FAIL_CRIT", "TWO_FIT_ALL_SPECS", "NONE_FIT_SPEC_REQ"))] %>% 
  .[,primary_doctor_npi := fifelse(primary_doctor==doctor_str1,
                                   doctor_npi_str1,
                                   doctor_npi_str2)]
```


```{r}
cscopy_final_bq <-  cscopy_final_bq[,.(
primary_doctor,
primary_doctor_npi,
most_important_fac	,
most_important_fac_npi,	
procedure_type,
procedure_modifier,
tp_med_med,
tp_med_surg,
tp_med_medi,
tp_med_path,
tp_med_radi,
tp_med_anes,
tp_med_faci,
ingest_date = Sys.Date()
)]
```


```{r, eval=FALSE}
bq_table_upload(x=procedure_table, values= cscopy_final_bq, create_disposition='CREATE_IF_NEEDED', write_disposition='WRITE_APPEND')
```
