---
title: Knee Replacement
author: Alexander Nielson
date: '2020-12-30'
slug: knee-replacement.en-us
categories:
  - Major Surgery
tags:
  - Knee
  - Replacement
keywords:
  - tech
---

# Introduction

In this section we will:  
* identify which Knee Replacement procedures were excluded and why
* identify which different Knee Replacement subgroups were created and why


If you have questions or concerns about this data please contact Alexander Nielson (alexnielson@utah.gov) 


# Load Libraries
Load Libraries
```{r, message=FALSE}
library(data.table)
library(tidyverse)
library(stringi)
library(ggridges)
library(broom)
library(disk.frame)
library(RecordLinkage)
library(googlesheets4)
library(bigrquery)
library(DBI)
devtools::install_github("utah-osa/hcctools2", upgrade="never" )
library(hcctools2)
```

Establish color palettes

```{r}
cust_color_pal1 <- c(
        "Anesthesia" = "#f3476f",
        "Facility" = "#e86a33",
        "Medicine Proc" = "#e0a426",
        "Pathology" = "#77bf45",
        "Radiology" = "#617ff7",
        "Surgery" = "#a974ee"
    )

cust_color_pal2 <- c(
        "TRUE" = "#617ff7",
        "FALSE" = "#e0a426"
    )

cust_color_pal3 <- c(
        "above avg" = "#f3476f",
        "avg" = "#77bf45",
        "below avg" = "#a974ee"
    )



  fac_ref_regex <- "(UTAH)|(IHC)|(HOSP)|(HOSPITAL)|(CLINIC)|(ANESTH)|(SCOPY)|(SURG)|(LLC)|(ASSOC)|(MEDIC)|(CENTER)|(ASSOCIATES)|(U OF U)|(HEALTH)|(OLOGY)|(OSCOPY)|(FAMILY)|(VAMC)|(SLC)|(SALT LAKE)|(CITY)|(PROVO)|(OGDEN)|(ENDO )|( VALLEY)|( REGIONAL)|( CTR)|(GRANITE)|( INSTITUTE)|(INSTACARE)|(WASATCH)|(COUNTY)|(PEDIATRIC)|(CORP)|(CENTRAL)|(URGENT)|(CARE)|(UNIV)|(ODYSSEY)|(MOUNTAINSTAR)|( ORTHOPEDIC)|(INSTITUT)|(PARTNERSHIP)|(PHYSICIAN)|(CASTLEVIEW)|(CONSULTING)|(MAGEMENT)|(PRACTICE)|(EMERGENCY)|(SPECIALISTS)|(DIVISION)|(GUT WHISPERER)|(INTERMOUNTAIN)|(OBGYN)"
```

# Connect to GCP database
```{r}
bigrquery::bq_auth(path = 'D:/gcp_keys/healthcare-compare-prod-95b3b7349c32.json')

# set my project ID and dataset name
project_id <- 'healthcare-compare-prod'
dataset_name <- 'healthcare_compare'

con <- dbConnect(
  bigrquery::bigquery(),
  project = project_id,
  dataset = dataset_name,
  billing = project_id
)
```


# Get NPI table
```{r}
query <-  paste0("SELECT npi, clean_name, osa_group, osa_class, osa_specialization
                 FROM `healthcare-compare-prod.healthcare_compare.npi_full`")
                       
#bq_project_query(billing, query) # uncomment to determine billing price for above query.

npi_full <- dbGetQuery(con, query) %>%
  data.table() 
```


# get a subset of the NPI providers based upon taxonomy groups
```{r}
gs4_auth(email="alexnielson@utah.gov")
```


```{r}
surgery <- read_sheet("https://docs.google.com/spreadsheets/d/1GY8lKwUJuPHtpUl4EOw9eriLUDG9KkNWrMbaSnA5hOU/edit#gid=0",
                    sheet="major_surgery") %>% as.data.table
surgery <-  surgery[is.na(Remove) ] %>% .[["NUCC Classification"]]
```

```{r}
  npi_prov_pair <-  npi_full[osa_class %in% surgery] %>% 
    .[,.(npi=npi,
         clean_name = clean_name
         )
      ] 
```


# Load Data

```{r}
bun_proc <-  disk.frame("full_apcd.df")
```

```{r}
knee <- bun_proc[surg_bun_t_knee == T & surg_bun_t_arthroplasty==T & surg_bun_sum_med > 2000]
```


```{r}
knee <- knee[duration_mean >=0]
```

```{r}
knee <-  knee[,`:=`(
  surg_sp_name_clean = surg_sp_npi %>% map_chr(get_npi_standard_name),
  surg_bp_name_clean = surg_bp_npi %>% map_chr(get_npi_standard_name),
  
  medi_sp_name_clean = medi_sp_npi %>% map_chr(get_npi_standard_name),
  medi_bp_name_clean = medi_bp_npi %>% map_chr(get_npi_standard_name),
  
  radi_sp_name_clean = radi_sp_npi %>% map_chr(get_npi_standard_name),
  radi_bp_name_clean = radi_bp_npi %>% map_chr(get_npi_standard_name),
  
  path_sp_name_clean = path_sp_npi %>% map_chr(get_npi_standard_name),
  path_bp_name_clean = path_bp_npi %>% map_chr(get_npi_standard_name),
  
  anes_sp_name_clean = anes_sp_npi %>% map_chr(get_npi_standard_name),
  anes_bp_name_clean = anes_bp_npi %>% map_chr(get_npi_standard_name),
  
  faci_sp_name_clean = faci_sp_npi %>% map_chr(get_npi_standard_name),
  faci_bp_name_clean = faci_bp_npi %>% map_chr(get_npi_standard_name)
                           )]
```

```{r}
knee %>% saveRDS("knee.RDS")
```

```{r}
#stop here
```

```{r}
knee <-  readRDS("knee.RDS")
```

We will first look at the distribution and high correlated tags. 
```{r}
knee %>% plot_med_density() %>% print()
knee %>% get_tag_cor() %>% print()
```

First thing to notice from the distribution is that we have a good chunk of knee surgeries that are under 5k. These are not reasonable estimates for the total knee replacements, and are likely only the surgeon costs (not the facility). 

From the correlation table we can see that the duration is quite influential in the price as is reflected in higher facility costs. 

Anesthesia presence also increases the cost. 

Lets examine the duration vs median price visually:


```{r}
knee %>% plot_price_vs_duration() %>% print()
```


Lets see what happens if we remove any of the lower end prices, that are essentially missing facility costs. The below code will filter out any bundled procedures that have a facility cost under 1000.

```{r}
knee <-  knee[faci_bun_sum_med > 1000]
```


```{r}
knee %>% plot_med_density() %>% print()
knee %>% get_tag_cor() %>% print()
```
this looks much better. We still need to filter out non standard bundles, but this is a much mor expected distribution. 

## antibody typing 

a pathology test that includes a antibody typing is higher correlated, so we will examine it
```{r}
knee %>% get_tag_density_information("path_bun_t_antibod") %>% print()
```
very few knee surgeries like this. It is not typical so they will be exluced from the standard 
```{r}
knee <-  knee[path_bun_t_antibod==F]
```

Once again lets look at the distribution of the knee surgeries with anesthesia and the correlated tags.
```{r}
knee %>% plot_med_density() %>% print()
knee %>% get_tag_cor() %>% print()
```
lets check the femur/resect/tumor bundle procs. I think this is rare so lets determine the number of surgeries like this:
```{r}
knee[surg_bun_t_femur==T] %>% nrow()
```
We can omit this one surgery from the standard. 

```{r}
knee <-  knee [surg_bun_t_femur==F]
```

Once again lets look at the distribution of the knee surgeries with anesthesia and the correlated tags.
```{r}
knee%>% plot_med_density() %>% print()
knee %>% get_tag_cor() %>% print()
```

facility charge with "subsequent hospital care"

```{r}
knee %>% get_tag_density_information("faci_bun_t_subsequent") %>% print()
```


```{r}
knee_at_sub_hosp <-  knee [faci_bun_t_subsequent==T]
knee <- knee[faci_bun_t_subsequent==F]
```


Once again lets look at the distribution of the knee surgeries with anesthesia and the correlated tags.
```{r}
knee%>% plot_med_density() %>% print()
knee %>% get_tag_cor() %>% print()
```

## Interlaminar Injection 
```{r}
knee %>% get_tag_density_information("surg_bun_t_lamina") %>% print()
```
there is not enough observations to warrant a separate group, but there is a signficnat difference in the types, so they will be excluded from the standard pool.
```{r}
knee <-  knee[surg_bun_t_lamina==F]
```

Once again lets look at the distribution of the knee surgeries with anesthesia and the correlated tags.
```{r}
knee%>% plot_med_density() %>% print()
knee %>% get_tag_cor() %>% print()
```
```{r}
knee[surg_bun_t_device==T] %>% nrow()
```
the number of bundled procedures that have a device removal is too rare.

```{r}
knee <- knee[surg_bun_t_device==F]
```


Once again lets look at the distribution of the knee surgeries with anesthesia and the correlated tags.
```{r}
knee%>% plot_med_density() %>% print()
knee %>% get_tag_cor() %>% print()
```

```{r}
knee[path_bun_t_without_scope==T] %>% nrow()
knee[surg_bun_t_revise==T] %>% nrow()
```
```{r}
knee <- knee[path_bun_t_without_scope==F & surg_bun_t_revise==F]
```

Once again lets look at the distribution of the knee surgeries with anesthesia and the correlated tags.
```{r}
knee%>% plot_med_density() %>% print()
knee %>% get_tag_cor() %>% print()
```

```{r}
knee %>% get_tag_density_information("radi_bun_t_echo") %>% print()
```

```{r}
knee%>% plot_med_density() %>% print()
knee %>% get_tag_cor() %>% print()
```



```{r}
knee_btbv4 <- knee %>% btbv4()
```


Get primary doctors


```{r}
knee_final_bq <- knee_btbv4[,
                     primary_doctor := pmap(.l=list(doctor_npi1=doctor_npi_str1,
                                  doctor_npi2=doctor_npi_str2,
                                  class_reqs="Orthopaedic Surgery"
                                  ),
                                                .f=calculate_primary_doctor) %>% as.character()
                     ] %>% 
  #Filter out any procedures where our doctors fail both criteria. 
  .[!(primary_doctor %in% c("BOTH_DOC_FAIL_CRIT", "TWO_FIT_ALL_SPECS"))] %>% 
  .[,primary_doctor_npi := fifelse(primary_doctor==doctor_str1,
                                   doctor_npi_str1,
                                   doctor_npi_str2)] %>% 
  .[,`:=`(
    procedure_type=2,
    procedure_modifier = "Standard Knee Replacement"
  )]
```


```{r}
knee_final_bq <- knee_final_bq[,.(
primary_doctor,
primary_doctor_npi,
most_important_fac	,
most_important_fac_npi,	
procedure_type,
procedure_modifier,
tp_med_med,
tp_med_surg,
tp_med_medi,
tp_med_path,
tp_med_radi,
tp_med_anes,
tp_med_faci,
ingest_date = Sys.Date()
)]
```

```{r, eval=FALSE}
bq_table_upload(x=procedure_table, values= knee_final_bq, create_disposition='CREATE_IF_NEEDED', write_disposition='WRITE_APPEND')
```

